---
title: "Differences in Resting-State Functional MRI Quality Control Recommendations Alter the Representativeness of the Adolescent Brain Cognitive Development (ABCD) Study"
subtitle: "Supplemental Methods and Results"
author: "Matthew Peverill1, Justin D. Russell, Taylor J. Keding, Hailey M. Rich, Max A. Halvorson, Kevin M. King, Rasmus Birn, & Ryan Herringa"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    number_sections: true
    keep_tex:  true
    toc_depth: 3
    latex_engine: xelatex
    keep_md: yes
classoption: landscape
header-includes: 
 \usepackage{geometry}
 \geometry{top=0.5in,left=.5in,bottom=0.5in,right=0.5in}
---

\listoftables
  
# Supplemental Methods

## Behavioral and Demographic Variables Detailed Information.

### Neighborhood Factors

Area Deprivation Index (ADI) is a composite measure of a neighborhood’s relative socioeconomic disadvantage as compared to other US neighborhoods (Singh, 2003). ADI has shown interactive effects with individual SES measures in predicting rs-fMRI functional connectivity in the ABCD dataset (Rakesh et al., 2021). The Child Opportunity Index (v2.0; COI2) is a composite index derived from census data that indexes neighborhood resources and conditions relevant to children’s development, inclusive of educational opportunities, health-affecting and environmental factors, and social and economic resources (Fan et al., 2021). When participants listed multiple residences, averages of these neighborhood factors were calculated and weighted according to time in residence.

### Trauma and Stress Exposure. 

Youth exposure to DSM-5 PTSD criterion-A eligible traumatic experiences, as measured by the parent-report Kiddie Schedule for Affective Disorders and Schizophrenia (KSADS; Townsend et al., 2020), was used as an index of traumatic stress exposure. We coded trauma exposure categorically as unexposed, single exposure, or multiple (two or more) exposures. This approach, when employed with a nationally representative sample of adolescents aged 13-17, roughly divided sample into tertiles for exposure severity (McLaughlin et al., 2013). This approach allows for specific examination of missingness among multiply exposed youth, who show especially high risk for PTSD (McLaughlin et al., 2013) and other adverse outcomes (Evans & Kim, 2010), and does so without dividing the sample into undersized sub-groups.

### Participant Demographics. 

Participant demographic variables included total family income, highest parental education, race/ethnicity, and sex assigned at birth. Income was re-leveled from ten income ranges to eight to allow for larger subject counts within each range (see Heeringa & Berglund, 2020). Caregiver education was similarly re-leveled from twenty-one levels to five; we expected minimal variation in exclusions within these five bins given findings from previous work with ABCD (Cosgrove et al., 2022). We used U.S. Census derived race/ethnicity categories included in ABCD to facilitate comparisons with existing literature (e.g., Cosgrove et al., 2022; Fadus et al., 2021; Heeringa & Berglund, 2020); notably, however, this approach may under-represent important U.S. sub-populations (Saragosa-Harris et al., 2022). Secondary analyses using the fully expanded variables are included in supplemental materials.


### Pubertal Development. 

We include pubertal development category scores (pre/early/mid/late/post-pubertal) derived from the Pubertal Development Scale (PDS; Petersen et al., 1988). We used the caregiver reported scores, as they may be more accurate in the age range (9-10 years) of the ABCD baseline sample (Cheng et al., 2021), but substituted child reported scores where caregiver reports were missing.

### Psychopathology. 

In order to separately examine the impact of general, internalizing, and externalizing psychopathology, we calculated a generalized psychopathology factor (P), as well as residual internalizing and externalizing factors, by fitting a bifactor model to the 8 subscales of the Child Behavior Checklist (CBCL; Achenbach et al., 2002; Brislin et al., 2021; D. A. Clark et al., 2021). The model showed acceptable fit to the data (χ² = 1338.249, df = 15, p < 0.001, RMSEA = 0.086, CFI = 0.973, TLI = 0.949, SRMR = 0.028). P-factor scores derived from the model were strongly correlated (r=.87) with the Total Problems subscale of the CBCL. 

### General Cognitive Ability. 

Cognitive ability was operationalized using the matrix reasoning task scaled score from the WISC-V as well as the cognition composite and crystalized intelligence composite scores captured by the NIH Toolbox (Akshoomoff et al., 2013; Thompson et al., 2019). Extant research affirms the reliability and validity of each measure in youth samples (Akshoomoff et al., 2013; Canivez et al., 2020; Thompson et al., 2019).

### Inhibitory Control. 

The NIH Toolbox Flanker Inhibitory Control task score (Weintraub et al., 2013) was included as a behavioral measure of inhibitory control. Scores on this task have been correlated with both parent reported hyperactivity and activity as measured by actigraphy in children with ADHD (Burley et al., 2022). 

# Code Supplement

This section includes R code used to generate all tables, figures, and statistics used in the main manuscript. Code is visible in the original Rmd document available (together with additional pre-processing code) on osf: https://osf.io/57xer/. The headings are hidden from the rendered document for legibility.

```{=latex}
% this will comment until \fi is called at the end of the code supplement.
\iffalse
```

       
```{r setup, include=FALSE}
library(tidyverse); library(ggthemes)
library(ggExtra)
library(pander)
library(hexbin)
library(huxtable)
library(viridis)
library(patchwork)
library(openxlsx)
library(ggupset)
library(lme4)
library(lmerTest)
library(emmeans)
requireNamespace("extrafont")
requireNamespace("openxlsx")
requireNamespace("grid")
requireNamespace("DescTools")
requireNamespace("sdlabFunctions") # https://github.com/mrpeverill/sdlabFunctions
requireNamespace("performance")
requireNamespace("parameters")
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE,dev = "cairo_pdf")
theme_set(theme_tufte(base_family = "Times New Roman"))
extrafont::loadfonts(quiet = TRUE)
huxtable::set_default_properties(latex_float="htbp")
```

```{r import}
recodesid <- function(x) {
  paste0("NDAR",substr(x, start = 6, stop = nchar(x)))
}

t1<-readRDS("ABCD-Data-Import/tabulateddata.Rds")
t2<-readRDS("ABCC_download/ABCCsubjectdata.RDS")
df<-left_join(readRDS("ABCD-Data-Import/tabulateddata.Rds") %>% 
                mutate(subjectkey=recodesid(as.character(subjectkey))),
              readRDS("ABCC_download/ABCCsubjectdata.RDS"),
              by=c("subjectkey"="sname"))
  
df<-df %>% 
  mutate(subjectkeychar=subjectkey,
         subjectkey=as.factor(subjectkey)) %>%  
  # Pt's without ABCC data should have FALSE for the 'Scan Exists' booleans
  mutate(across(starts_with("Exists"),
                ~ case_when(. == "True" ~ TRUE,
                            . == "False" ~ FALSE,
                            is.na(.) ~ FALSE))) %>%
  # Pt's without ABCC data should have TRUE for > 5 minute data booleans.
  mutate(across(starts_with("ltfive"),
                ~ replace_na(.,TRUE))) %>% 
  #Standardize psychopathology scores
  mutate(across(pfactor:EXT,scale)) %>% 
  # Are there any rsfmri images in ABCC?
  mutate(any_rest = (Exists_rest_1 |
                     Exists_rest_2 |
                     Exists_rest_3 |
                     Exists_rest_4)) %>% 
  #Are there >375 low motion frames per threshold 
  mutate(across(starts_with("gframes"),\(x) {x>375},.names = "{.col}_375")) %>% 
  mutate(across(ends_with("375"),~replace_na(.,FALSE)))

imgincl<-readRDS("ABCD-fastqc01/imginclusion.Rds")

df<-left_join(df,imgincl[,1:2],by=join_by(subjectkeychar==subjectkey)) %>% 
  mutate(fastqcok=replace_na(fastqcok,FALSE))

# N.B. A few (8) Pt's have neuroimaging data but not tabular data.
# Possibly they have removed consent? They are not included in this
# analysis
```

```{r analysis-preferences}
options(tinytex.clean = FALSE)
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

## Additional Coding and Releveling

```{r}
cvars <- c(
    "adi",
    "coi",
    "nihtbx_flanker_agecorrected",
    "nihtbx_cryst_agecorrected",
    "nihtbx_totalcomp_agecorrected",
    "pea_wiscv_tss",
    "pfactor",
    "INT",
    "EXT",
    "interview_age",
    "bmi"
  )

# Z scores
df <- df %>% mutate(across(ends_with(cvars),scale,.names = "{.col}.z"))

# Relevel factors to set comparison to modal levels

df$p.edu<-relevel(factor(df$p.edu,ordered=FALSE),4)
df$household.income<-relevel(df$household.income,5)

```

## Descriptives

### Figure 1: Condition Descriptions, inclusion counts, and inconsistencies


```{r}
setsdf<- df %>%
  select(c(subjectkey,ABCD_rsfmri_QC1,ABCD_rsfmri_QC2,any_rest)) %>%
  rename("T"="ABCD_rsfmri_QC1",
         "R"="ABCD_rsfmri_QC2",
         "C"="any_rest") %>% 
  rowwise %>% 
  mutate(sets = list(names(select(.,
            where(is.logical)))[c_across(where(is.logical))])) %>%
       ungroup 

```

Figure 1 panel b:

```{r}
# This code also generates table 1
levelsdf<-data.frame(
  Level = c(
    "Full (F)",
    "ABCD 4 Tabulated (T)",
    "ABCC (C)",
    "ABCC < .5mm",
    "ABCC < .4mm",
    "ABCC < .3mm",
    "ABCD 4 Recommended (R)",
    "ABCD < .2mm",
    "ABCD < .1mm"
  ),
  Description = c(
    "Entire sample",
    "rsFMRI tabulated data available (at least 1 T1 and 1 rsFMRI were complete and passed visual inspection)",
    "rs-fMRI data in the ABCD Community Collection",
    "ABCC + censoring at threshold*",
    "\"",
    "\"",
    "T1 and rs-fMRI recommended in 'ABCD Recommended Imaging Inclusion' table (includes 375 frames at <.2mm FD)",
    "ABCC + censoring at .2mm threshold",
    "\""
  ),
  Count = c(
    nrow(df),
    sum(df$ABCD_rsfmri_QC1),
    sum(df$any_rest),
    sum(df$gframes_0.5_375),
    sum(df$gframes_0.4_375),
    sum(df$gframes_0.3_375),
    sum(df$ABCD_rsfmri_QC2),
    sum(df$gframes_0.2_375),
    sum(df$gframes_0.1_375)
  )
)

levelsdf$Levelf<-factor(levelsdf$Level,levels=c(
    "Full (F)",
    "ABCD 4 Tabulated (T)",
    "ABCC (C)",
    "ABCC < .5mm",
    "ABCC < .4mm",
    "ABCC < .3mm",
    "ABCD 4 Recommended (R)",
    "ABCD < .2mm",
    "ABCD < .1mm"
  ),
  labels = c(
    "Full (**F**)",
    "ABCD 4 Tabulated (**T**)",
    "ABCC (**C**)",
    "ABCC < **.5**mm",
    "ABCC < **.4**mm",
    "ABCC < **.3**mm",
    "ABCD 4 Recommended (**R**)",
    "ABCC < **.2**mm",
    "ABCC < **.1**mm"
  ))

library(ggtext)
samplecounts<-ggplot(levelsdf,aes(x=Levelf,y=Count,label=Count)) +
  labs(title="B. n by Condition") + 
  geom_point(color="#c5050c",size=4,alpha=0.6) +
  geom_segment(aes(x=Levelf,xend=Levelf,y=0,yend=Count),color="#646569") +
  scale_x_discrete(limits = rev(levels(levelsdf$Levelf))) +
  coord_flip() +
  theme(axis.ticks.y=element_blank(),
        axis.title.y=element_blank(),
        axis.title.x=element_blank(),
        axis.text.y=element_markdown(),
        plot.title=element_text()) +
  geom_text(nudge_x = .25,nudge_y=-1500,family="Times New Roman")

```

Figure 1 panel C:

```{r}
upsetfig<-ggplot(setsdf,aes(x=sets)) +
  theme(axis.title.x = element_blank()) +
  ggtitle("C. Inclusion Inconsistencies ") +
  ylab("n") +
  geom_bar() +
  geom_text(stat='count',
            aes(label=after_stat(count)),
            vjust=-.5,
            size=10 / .pt,
            family="Times New Roman") +
  expand_limits(y=c(0,8800)) +
  scale_x_upset()
```


```{r}
ggsave("Manuscript/Figures/inclusioncounts.svg",
       (plot_spacer() + (samplecounts / upsetfig + plot_layout(heights=c(3,2)))) +
         plot_layout(widths=c(3,2)),
       width=7.5,height=5)
```

(panel A is added using a vector graphics program.)

### Categorical Variable Figure (Figure 2)

```{r}
bools<-c("full", 
         "ABCD_rsfmri_QC1",
         "any_rest",
         "gframes_0.5_375",
         "gframes_0.4_375",
         "gframes_0.3_375",
         "ABCD_rsfmri_QC2",
         "gframes_0.2_375",
         "gframes_0.1_375")

catvars<-c("sex",
             "household.income",
             "p.edu",
             "race_ethnicity.factor",
             "ksads_factor",
             "pds_category")

#This replaces NA with 'missing' for tabulation and reverses the scrubbing vars.

dfcatna <- df %>% select(c(ends_with(catvars), ends_with(bools))) %>%
  mutate(across(
    ends_with(catvars),
    ~ factor(
      .x,
      levels = levels(addNA(.x)),
      labels = c(levels(.x), "Missing"),
      exclude = NULL
    )
  ))

catvar375figdf<-data.frame(variable=character(),
                         level=character())
for (var in catvars) {
  levels <- levels(dfcatna[[var]])
  var_df <- data.frame(
    variable = var,
    level = levels
  )
  # Append the data frame to the levels_df
  catvar375figdf <- rbind(catvar375figdf, var_df)
}

dfcatna$full=TRUE

for(b in bools) {
  n<-sum(dfcatna[,b])
  v<-sapply(1:nrow(catvar375figdf),\(x) {
    vname<-catvar375figdf[x,"variable"]
    tlevel<-catvar375figdf[x,"level"]
    vmatch<-dfcatna[[vname]]==tlevel
    sum(vmatch & dfcatna[[b]])/n
  })
  catvar375figdf[,b]<-v*100
}
  
catvar375figdflong <- catvar375figdf %>% 
  pivot_longer(full:gframes_0.1_375) %>% 
  mutate(thresh=factor(name,levels=bools,labels=c("F",
                                                  "T",
                                                  "C",
                                                  ".5",
                                                  ".4",
                                                  ".3",
                                                  "R",
                                                  ".2",
                                                  ".1"))) %>% 
  mutate(levelf=as.factor(level)) %>% 
  mutate(variable=as.factor(variable))

cp1<-catvar375figdflong %>% 
  filter(variable=="sex") %>% 
  mutate(level=as.factor(level)) %>% 
  ggplot(aes(x=thresh,y=value,fill=level)) +
      geom_bar(position="fill",stat="identity") +
      scale_fill_viridis(discrete = TRUE) +
      labs(title="Sex Assigned at Birth") +
      theme(axis.title.y=element_blank(),
            axis.text.y=element_blank(),
            axis.title.x=element_blank(),
            axis.ticks.y=element_blank(),
            legend.title=element_blank())

cp2<-catvar375figdflong %>% 
  filter(variable=="household.income") %>% 
  mutate(level=factor(level,levels=levels(dfcatna$household.income))) %>% 
  ggplot(aes(x=thresh,y=value,fill=level)) +
      geom_bar(position="fill",stat="identity") +
      scale_fill_viridis(discrete = TRUE) +
      labs(title="Household Income") +
      theme(axis.title.y=element_blank(),
            axis.text.y=element_blank(),
            axis.title.x=element_blank(),
            axis.ticks.y=element_blank(),
            legend.title=element_blank())

cp3<-catvar375figdflong %>% 
  filter(variable=="race_ethnicity.factor") %>% 
  mutate(level=factor(level,levels=levels(dfcatna$race_ethnicity.factor))) %>% 
  ggplot(aes(x=thresh,y=value,fill=level)) +
      geom_bar(position="fill",stat="identity") +
      scale_fill_viridis(discrete = TRUE) +
      labs(title="Census Race/Ethnicity") +
      theme(axis.title.y=element_blank(),
            axis.text.y=element_blank(),
            axis.title.x=element_blank(),
            axis.ticks.y=element_blank(),
            legend.title=element_blank())

cp4<-catvar375figdflong %>% 
  filter(variable=="ksads_factor") %>% 
  mutate(level=as.factor(level)) %>% 
  ggplot(aes(x=thresh,y=value,fill=level)) +
      geom_bar(position="fill",stat="identity") +
      scale_fill_viridis(discrete = TRUE) +
      labs(title="Trauma Count") +
      theme(axis.title.y=element_blank(),
            axis.text.y=element_blank(),
            axis.title.x=element_blank(),
            axis.ticks.y=element_blank(),
            legend.title=element_blank())


cp5<-catvar375figdflong %>% 
  filter(variable=="pds_category") %>% 
  mutate(level=factor(level,levels=levels(dfcatna$pds_category))) %>% 
  ggplot(aes(x=thresh,y=value,fill=level)) +
      geom_bar(position="fill",stat="identity") +
      scale_fill_viridis(discrete = TRUE) +
      labs(title="Pubertal Status") +
      theme(axis.title.y=element_blank(),
            axis.text.y=element_blank(),
            axis.title.x=element_blank(),
            axis.ticks.y=element_blank(),
            legend.title=element_blank())

cp6<-catvar375figdflong %>% 
  filter(variable=="p.edu") %>% 
  mutate(level=factor(level,levels=levels(dfcatna$p.edu))) %>% 
  ggplot(aes(x=thresh,y=value,fill=level)) +
      geom_bar(position="fill",stat="identity") +
      scale_fill_viridis(discrete = TRUE) +
      labs(title="Parent Education") +
      theme(axis.title.y=element_blank(),
            axis.title.x=element_blank(),
            axis.text.y=element_blank(), 
            axis.ticks.y=element_blank(),
            legend.title=element_blank())
```

```{r}

svg(filename="Manuscript/Figures/CatVarFig.svg",height=9,width=7.5,family="Times New Roman")

((cp1 / cp4 / cp3) |
  (cp2 / cp6 / cp5))
grid::grid.draw(grid::textGrob("Proportion at Threshold",x=.01,rot=90,gp = grid::gpar(fontfamily = "Times New Roman")))
grid::grid.draw(grid::textGrob("QC Threshold",y=.01,gp = grid::gpar(fontfamily = "Times New Roman")))

dev.off()
```

### Continuous Variables Figure (Figure 3)

```{r}
# we need ymin, ymax, lower, upper, and middle for each variable in each condition.
#we need ymin, ymax, lower, upper, and middle for each variable in each condition.
bpstats <- function(var,bool) {
  #message(paste0("var is ",var))   
  #message(paste0("bool is ",bool))
  x<-df[df[[bool]],var]
  minvalue=min(x,na.rm=TRUE)
  maxvalue=max(x,na.rm=TRUE)
  median=median(x,na.rm = TRUE)
  low=quantile(x,.25,na.rm=TRUE)
  high=quantile(x,.75,na.rm=TRUE)
  IQR=high-low
  mn=max(low-1.5*IQR,minvalue)
  mx=min(high+1.5*IQR,maxvalue)
  return(data.frame(lwhisk=mn,low=low,median=median,high=high,uwhisk=mx))
}

cvars <- c(
    "adi.z",
    "coi.z",
    "nihtbx_flanker_agecorrected.z",
    "nihtbx_cryst_agecorrected.z",
    "nihtbx_totalcomp_agecorrected.z",
    "pea_wiscv_tss.z",
    "pfactor.z",
    "INT.z",
    "EXT.z",
    "interview_age.z",
    "bmiAgeZ"
  )

  df$full=TRUE

ContFig375df<-expand.grid(as.factor(cvars),unique(bools)) %>%
  mutate(Var1 = as.character(Var1),
         Var2 = as.character(Var2)) %>%
  rowwise() %>%
  mutate(bpstats(Var1,Var2))

ContFig375df$measp<-factor(ContFig375df$Var1,
                           levels=cvars,
                           labels=c("Area Disadvantage",
                                    "Child Opportunity",
                                    "NIHTB Flanker",
                                    "NIHTB Crystalized",
                                    "NIHTB Total",
                                    "WISC V Matrix",
                                    "Psychopathology (p)",
                                    "Internalizing",
                                    "Externalizing",
                                    "Age",
                                    "BMI"))

ContFig375df$thresh <- factor(
  ContFig375df$Var2,
  levels = bools,
  labels = c("F",
             "T",
             "C",
             ".5",
             ".4",
             ".3",
             "R",
             ".2",
             ".1")
)

ggsave("Manuscript/Figures/ContVarFig.svg",
       ggplot(
         ContFig375df,
         aes(
           x = thresh,
           ymin = lwhisk,
           lower = low,
           middle = median,
           upper = high,
           ymax = uwhisk
         )
       ) +
         geom_boxplot(stat = "identity") +
         ylab("Z") +
         theme(axis.title.x = element_blank()) +
         facet_wrap( ~ measp, scales = "free"),
       height = 5, width = 7.5)

```

### Trauma Count

We describe trauma count statistics in our methods:

`r table(df$ksads_factor)`

## Table: Associations of behavioral data with framewise displacement (Table 1 and 2)

```{r}
ccor<-df %>% select("adi.z",
    "coi.z",
    "nihtbx_flanker_agecorrected.z",
    "nihtbx_cryst_agecorrected.z",
    "nihtbx_totalcomp_agecorrected.z",
    "pea_wiscv_tss.z",
    "pfactor.z",
    "INT.z",
    "EXT.z",
    "interview_age.z",
    "bmiAgeZ",
    filtered_fd_0.1:filtered_fd_0.5) %>% 
  sdlabFunctions::sdcorr()

#This is the version in the manuscript.
write.csv(ccor[1:11,19:30],"Manuscript/Tables/FDcorr_continuousDVs2.csv",row.names=TRUE)

# This will write tables of bivariate linear models of FD with both continuous and discrete variables::

# Updated colnames for vars
y_names = c("filtered_fd_0.1","filtered_fd_0.2","filtered_fd_0.3","filtered_fd_0.4","filtered_fd_0.5")
x_names = c("adi","coi","nihtbx_flanker_agecorrected","nihtbx_cryst_agecorrected","nihtbx_totalcomp_agecorrected",
             "pea_wiscv_tss","pfactor","INT","EXT","interview_age","bmiAgeZ","sex","household.income","p.edu",
             "race_ethnicity.factor","ksads_factor","pds_category")

contOut = data.frame("IV"=c(),"DV"=c(),"BETA"=c(),"STD_BETA"=c(),"R_SQU"=c(),"T"=c(),"P"=c())
discOut = data.frame("IV"=c(),"DV"=c(),"F"=c(),"DF_1"=c(),"DF_2"=c(),"MODEL_P"=c(),"CONTRAST"=c(),"BETA"=c(),"SE"=c(),"T-RATIO"=c(),"P"=c())

# Iterate dependent variables (motion thresholds)
for(y_name in y_names){
  # Iterate independent variables
  for(x_name in x_names){
    
    # Create dataframe with only variables of interest, remove NAs
    temp_df = na.omit(data.frame(y_name=df[y_name],x_name=df[x_name]))
    
    # For continuous predictors:
    if( !(x_name %in% c("sex","household.income","p.edu","race_ethnicity.factor","ksads_factor","pds_category"))){
      
      # Scale
      temp_df[x_name] = scale(temp_df[x_name],center=TRUE,scale=TRUE)
      
      # Build a model
      mod = lm(data=temp_df,paste0(y_name,"~",x_name))
      modTemp = summary(mod)
      
      # Append statistics
      contOut = rbind(contOut,data.frame(
        "IV"=y_name,"DV"= x_name,"BETA"=modTemp$coefficients[2],"STD_BETA"=as.numeric(QuantPsyc::lm.beta(mod)),"R_SQU"=modTemp$r.squared,
        "T"=modTemp$coefficients[6],"P"=modTemp$coefficients[8]
      ))
    }
    
    # For discrete predictors:
    else{
      
      # Build a model
      mod = lm(data=temp_df,paste0(y_name,"~",x_name))
      modTemp = summary(mod)
      #post_hoc = data.frame(emmeans::emmeans(mod,reformulate(x_name, 'pairwise'))$contrasts)[,c(1,2,3,5,6)]
      post_hoc = data.frame(emmeans::emmeans(mod,reformulate(x_name, 'trt.vs.ctrl1'))$contrasts)[,c(1,2,3,5,6)]
      
      
      # Format and append statistics
      colnames(post_hoc) = c("CONTRAST","BETA","SE","T-RATIO","P")
      mod_stats = data.frame("IV"=rep(y_name,nrow(post_hoc)),
                             "DV"=rep(x_name,nrow(post_hoc)),
                             "F"=rep(as.numeric(modTemp$fstatistic[1]),nrow(post_hoc)),
                             "DF_1"=rep(as.numeric(modTemp$fstatistic[2]),nrow(post_hoc)),
                             "DF_2"=rep(modTemp$fstatistic[3],nrow(post_hoc)),
                             "MODEL_P"=rep(pf(as.numeric(modTemp$fstatistic[1]),as.numeric(modTemp$fstatistic[2]),
                                                         as.numeric(modTemp$fstatistic[3]),lower.tail = FALSE),nrow(post_hoc)))
      discOut = rbind(discOut,cbind(mod_stats,post_hoc))
    }

  }
}

sdfd <- t(df %>%
  summarize(
    sd_fd_0.1 = sd(filtered_fd_0.1, na.rm = TRUE),
    sd_fd_0.2 = sd(filtered_fd_0.2, na.rm = TRUE),
    sd_fd_0.3 = sd(filtered_fd_0.3, na.rm = TRUE),
    sd_fd_0.4 = sd(filtered_fd_0.4, na.rm = TRUE),
    sd_fd_0.5 = sd(filtered_fd_0.5, na.rm = TRUE)
  ))

discOut$fdsd<-rep(sdfd,each=sum(discOut$IV=="filtered_fd_0.1"))
discOut$sBeta<-discOut$BETA/discOut$fdsd

# Write tables to csv This continuous table did not end up included in the manuscirpt.
write.csv(contOut,"Manuscript/Tables/FDcorr_continuousDVs.csv",row.names=FALSE)
write.csv(discOut,"Manuscript/Tables/FDcorr_discreteDVs.csv",row.names=FALSE)
```

## Bivariate Models and Table

```{r}
ORformat<-\(x) {DescTools::Format(exp(x),digits=2,ldigits=0)}
pformat<-\(x) {DescTools::Format(x,digits=3,ldigits=0,sci=30)}

varstring <-
  c(
    "sex",
    "household.income",
    "p.edu",
    "race_ethnicity.factor",
    "ksads_factor",
    "pds_category",
    "adi.z",
    "coi.z",
    "nihtbx_flanker_agecorrected.z",
    "nihtbx_cryst_agecorrected.z",
    "nihtbx_totalcomp_agecorrected.z",
    "pea_wiscv_tss.z",
    "pfactor.z",
    "INT.z",
    "EXT.z",
    "interview_age.z",
    "bmiAgeZ"
  )

bvmodel <- \(x,newline="\n") {
  cstrings <-
    c(
      "!ABCD_rsfmri_QC1",
      "!any_rest",
      "!gframes_0.5_375",
      "!gframes_0.4_375",
      "!gframes_0.3_375",
      "!ABCD_rsfmri_QC2",
      "!gframes_0.2_375",
      "!gframes_0.1_375"
    )
  model.list<-sapply(cstrings,\(y) glm(as.formula(paste0(y," ~ ",x)),data=df,family="binomial"),simplify=FALSE)
  sapply(model.list,
         \(x) {
           lf<-length(coef(x))
           if(lf==2) {
             table<-t(c(coef=coef(x)[2:lf],
                        confint(x,2:lf,level=.95),
                        p=coef(summary(x))[2:lf,4]))
           } else {
             table<-cbind(coef=coef(x)[2:lf],
                        confint(x,2:lf,level=.95),
                        p=coef(summary(x))[2:lf,4])
           }
           
           #Bonferonni correction
           if(names(coef(x))[2] %in% c("adi.z",
                                       "coi.z",
                                       "nihtbx_totalcomp_agecorrected.z",
                                       "pea_wiscv_tss.z")) {
             table[,4]<-table[,4]*2
           }
           m<-paste0(ORformat(table[,1]),
                                sdlabFunctions::starPs(table[,4]),
                                newline,
                                ORformat(table[,2]),
                                "-",
                                ORformat(table[,3]),
                                newline,
                                pformat(table[,4]))
           names(m)<-names(coef(x)[2:lf])
           sub(".000","<.001",m)
    },
    simplify=TRUE)
}

bvtable<-reduce(sapply(varstring,bvmodel),rbind)

alllevels<-c(
  "Sex (Male)",
      "  $0-$25k",
      "  $25-$50k",
      "  $50-$75k",
      "  $75-$100k",
      "  >$200k",
      "  <High School",
      "  HS Grad.",
      "  Some College",
      "  Graduate",
      "  Black",
      "  Hispanic",
      "  Asian",
      "  Other",
      "  1 Trauma",
      "  >=2 Trauma",
      "  Early Puberty",
      "  Mid Puberty",
      "  Late Puberty",
      "  Post Pubertal",
      "Area Disadvantage",
      "Child Opportunity",
      "NIHTB Flanker",
      "NIHTB Crystalized",
      "NIHTB Total",
      "WISC V Matrix",
      "Psychopathology",
      "Internalizing",
      "Externalizing",
      "Age",
      "BMI"
)


#1 column per level
bvhux <- as_hux(bvtable) %>%
  insert_column(alllevels) %>%
  insert_row(
    "Household Income (ref: $100-$200k)",
    after = 1,
    colspan = 9,
    fill = ""
  ) %>%
  insert_row(
    "Highest Parental Education (ref: College Degree)",
    after = 7,
    colspan = 9,
    fill = ""
  ) %>%
  insert_row(
    "Census Race/Ethnicity (ref: White)",
    after = 12,
    colspan = 9,
    fill = ""
  ) %>%
  insert_row(
    "KSADS Trauma Count (ref: 0 Exposures)",
    after = 17,
    colspan = 9,
    fill = ""
  ) %>%
  insert_row(
    "Pubertal Status (ref: pre-pubertal)",
    after = 20,
    colspan = 9,
    fill = ""
  ) %>%
  insert_row(c("Variable", rep(c("OR\n[90% CI]\np"), 8)), after = 0) %>%
  insert_row(c("", "T", "C", ".5", ".4", ".3", "R", ".2", ".1"))

tables.xlsx<-openxlsx::createWorkbook()
tables.xlsx<-as_Workbook(bvhux[1:20,],
                     Workbook=tables.xlsx,
                     sheet="bvmPage1")
tables.xlsx<-as_Workbook(bvhux[c(1:2,21:nrow(bvhux)),],
                     Workbook=tables.xlsx,
                     sheet="bvmPage2")

```


## Condition (Adjusted) Models 

```{r}
#terms 22 and 23 (neighborhood factors), as well as term 26 and 27 (general cognition measures) need to be corrected.
pcorrect<-\(x) {
  x[22:23]<-x[22:23]*2
  x[26:27]<-x[26:27]*2
  x
}

adjmodelrightterms<-"~ sex + household.income + p.edu + race_ethnicity.factor + 
ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z + 
nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + 
pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z + bmiAgeZ"
model.QC1 <-
  glm(as.formula(paste("!ABCD_rsfmri_QC1 ", adjmodelrightterms)),
      data = df, family = "binomial")
model.QC1.results <-
  cbind(confint(model.QC1, level = .95), model.QC1$coefficients)[, c(1, 3, 2)]
model.QC1.results <-
  cbind(model.QC1.results, pcorrect(coef(summary(model.QC1))[, 4]))

model.ABCC <-
  glm(as.formula(paste("!any_rest ", adjmodelrightterms)), data = df, family =
        "binomial")
model.ABCC.results <-
  cbind(confint(model.ABCC, level = .95), model.ABCC$coefficients)[, c(1, 3, 2)]
model.ABCC.results <-
  cbind(model.ABCC.results, pcorrect(coef(summary(model.ABCC))[, 4]))

model.5mm <-
  glm(as.formula(paste("!gframes_0.5_375 ", adjmodelrightterms)), data = df, family =
        "binomial")
model.5mm.results <-
  cbind(confint(model.5mm, level = .95), model.5mm$coefficients)[, c(1, 3, 2)]
model.5mm.results <-
  cbind(model.5mm.results, pcorrect(coef(summary(model.5mm))[, 4]))

model.4mm <-
  glm(as.formula(paste("!gframes_0.4_375 ", adjmodelrightterms)), data = df, family =
        "binomial")
model.4mm.results <-
  cbind(confint(model.4mm, level = .95), model.4mm$coefficients)[, c(1, 3, 2)]
model.4mm.results <-
  cbind(model.4mm.results, pcorrect(coef(summary(model.4mm))[, 4]))

model.3mm <-
  glm(as.formula(paste("!gframes_0.3_375 ", adjmodelrightterms)), data = df, family =
        "binomial")
model.3mm.results <-
  cbind(confint(model.3mm, level = .95), model.3mm$coefficients)[, c(1, 3, 2)]
model.3mm.results <-
  cbind(model.3mm.results, pcorrect(coef(summary(model.3mm))[, 4]))

model.QC2 <-
  glm(as.formula(paste("!ABCD_rsfmri_QC2 ", adjmodelrightterms)), data = df, family =
        "binomial")
model.QC2.results <-
  cbind(confint(model.QC2, level = .95), model.QC2$coefficients)[, c(1, 3, 2)]
model.QC2.results <-
  cbind(model.QC2.results, pcorrect(coef(summary(model.QC2))[, 4]))

model.2mm <-
  glm(as.formula(paste("!gframes_0.2_375 ", adjmodelrightterms)), data = df, family =
        "binomial")
model.2mm.results <-
  cbind(confint(model.2mm, level = .95), model.2mm$coefficients)[, c(1, 3, 2)]
model.2mm.results <-
  cbind(model.2mm.results, pcorrect(coef(summary(model.2mm))[, 4]))


model.1mm <-
  glm(as.formula(paste("!gframes_0.1_375 ", adjmodelrightterms)), data = df, family =
        "binomial")
model.1mm.results <-
  cbind(confint(model.1mm, level = .95), model.1mm$coefficients)[, c(1, 3, 2)]
model.1mm.results <-
  cbind(model.1mm.results, pcorrect(coef(summary(model.1mm))[, 4]))
```

### Adjusted Model Tables

```{r}
Mformat<-\(m) {
  stars<-sdlabFunctions::starPs(m[,4])
  paste0(ORformat(m[,2]),
         stars,
         "\n",ORformat(m[,1]),"-",ORformat(m[,3]),"",
         "\n",DescTools::Format(m[,4],digits=3,ldigits=0,sci=30))
}

h1modelstable<-cbind(Mformat(model.QC1.results),
                     Mformat(model.ABCC.results),
                     Mformat(model.5mm.results),
                     Mformat(model.4mm.results),
                     Mformat(model.3mm.results),
                     Mformat(model.QC2.results),
                     Mformat(model.2mm.results),
                     Mformat(model.1mm.results))

h1modelstable[h1modelstable==".000"]<-"<.001"

alllevels<-c("Intercept",
      "Sex (Male)",
      "  $0-$25k",
      "  $25-$50k",
      "  $50-$75k",
      "  $75-$100k",
      "  >$200k",
      "  <High School",
      "  HS Grad.",
      "  Some College",
      "  Graduate",
      "  Black",
      "  Hispanic",
      "  Asian",
      "  Other",
      "  1 Trauma",
      "  >=2 Trauma",
      "  Early Puberty",
      "  Mid Puberty",
      "  Late Puberty",
      "  Post Pubertal",
      "Area Disadvantage",
      "Child Opportunity",
      "NIHTB Flanker",
      "NIHTB Crystalized",
      "NIHTB Total",
      "WISC V Matrix",
      "Psychopathology",
      "Internalizing",
      "Externalizing",
      "Age",
      "BMI"
      )

#1 column per level
h1hux <- as_hux(h1modelstable) %>%
  insert_column(alllevels) %>%
  insert_row(
    "Household Income (ref: $100-$200k)",
    after = 2,
    colspan = 9,
    fill = ""
  ) %>%
  insert_row(
    "Highest Parental Education (ref: College Degree)",
    after = 8,
    colspan = 9,
    fill = ""
  ) %>%
  insert_row(
    "Census Race/Ethnicity (ref: White)",
    after = 13,
    colspan = 9,
    fill = ""
  ) %>%
  insert_row(
    "KSADS Trauma Count (ref: 0 Exposures)",
    after = 18,
    colspan = 9,
    fill = ""
  ) %>%
  insert_row(
    "Pubertal Status (ref: pre-pubertal)",
    after = 21,
    colspan = 9,
    fill = ""
  ) %>%
  insert_row(c("Variable", rep(c("OR\n[90% CI]\np"), 8)), after = 0) %>%
  insert_row(c("", "T", "C", ".5", ".4", ".3", "R", ".2", ".1"))

colnames(h1hux)[1]<-"h1"

tables.xlsx<-as_Workbook(h1hux[1:20,],
                     Workbook=tables.xlsx,
                     sheet="AdjustedModels1")
tables.xlsx<-as_Workbook(h1hux[c(1:2,21:nrow(h1hux)),],
                     Workbook=tables.xlsx,
                     sheet="AdjustedModels2")

```

### Site and MRI Effects -- sensitivity analysis.

These are run only in some conditions: ABCC, QC2, 2mm

```{r}
model.ABCC.scanner<-glm(
  !any_rest ~ sex + household.income + p.edu + race_ethnicity.factor + 
    ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z 
    + nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + 
    pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z + bmiAgeZ + 
    mri_model,
  data=df,
  family="binomial")
model.ABCC.scanner.results<-cbind(confint(model.ABCC.scanner,level=.95),model.ABCC.scanner$coefficients)[,c(1,3,2)]
model.ABCC.scanner.results<-cbind(model.ABCC.scanner.results,p.adjust(coef(summary(model.ABCC.scanner))[,4],method="fdr"))

model.ABCC.scanner.site<-glm(
  !any_rest ~ sex + household.income + p.edu + race_ethnicity.factor + 
    ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z 
    + nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + 
    pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z + bmiAgeZ + 
    mri_model + site_id_l,
  data=df,
  family="binomial")
model.ABCC.scanner.site.results<-cbind(confint(model.ABCC.scanner.site,level=.95),model.ABCC.scanner.site$coefficients)[,c(1,3,2)]
model.ABCC.scanner.site.results<-cbind(model.ABCC.scanner.site.results,p.adjust(coef(summary(model.ABCC.scanner.site))[,4],method="fdr"))

model.2mm.scanner<-glm(
  !gframes_0.2_375 ~ sex + household.income + p.edu + race_ethnicity.factor + 
    ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z 
    + nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + 
    pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z + bmiAgeZ + 
    mri_model,
  data=df,
  family="binomial")
model.2mm.scanner.results<-cbind(confint(model.2mm.scanner,level=.95),model.2mm.scanner$coefficients)[,c(1,3,2)]
model.2mm.scanner.results<-cbind(model.2mm.scanner.results,p.adjust(coef(summary(model.2mm.scanner))[,4],method="fdr"))

model.2mm.scanner.site<-glm(
  !gframes_0.2_375 ~ sex + household.income + p.edu + race_ethnicity.factor + 
    ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z 
    + nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + 
    pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z + bmiAgeZ + 
    mri_model + site_id_l,
  data=df,
  family="binomial")
model.2mm.scanner.site.results<-cbind(confint(model.2mm.scanner.site,level=.95),model.2mm.scanner.site$coefficients)[,c(1,3,2)]
model.2mm.scanner.site.results<-cbind(model.2mm.scanner.site.results,p.adjust(coef(summary(model.2mm.scanner.site))[,4],method="fdr"))

model.QC2.scanner<-glm(
  !ABCD_rsfmri_QC2 ~ sex + household.income + p.edu + race_ethnicity.factor + 
    ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z 
    + nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + 
    pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z + bmiAgeZ + 
    mri_model,
  data=df,
  family="binomial")
model.QC2.scanner.results<-cbind(confint(model.QC2.scanner,level=.95),model.QC2.scanner$coefficients)[,c(1,3,2)]
model.QC2.scanner.results<-cbind(model.QC2.scanner.results,p.adjust(coef(summary(model.QC2.scanner))[,4],method="fdr"))

model.QC2.scanner.site<-glm(
  !ABCD_rsfmri_QC2 ~ sex + household.income + p.edu + race_ethnicity.factor + 
    ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z 
    + nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + 
    pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z + bmiAgeZ + 
    mri_model + site_id_l,
  data=df,
  family="binomial")
model.QC2.scanner.site.results<-cbind(confint(model.QC2.scanner.site,level=.95),model.QC2.scanner.site$coefficients)[,c(1,3,2)]
model.QC2.scanner.site.results<-cbind(model.QC2.scanner.site.results,p.adjust(coef(summary(model.QC2.scanner.site))[,4],method="fdr"))

model.ABCC.site<-glm(
  !any_rest ~ sex + household.income + p.edu + race_ethnicity.factor + 
    ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z 
    + nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + 
    pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z + bmiAgeZ + 
    site_id_l,
  data=df,
  family="binomial")
model.ABCC.site.results<-cbind(confint(model.ABCC.site,level=.95),model.ABCC.site$coefficients)[,c(1,3,2)]
model.ABCC.site.results<-cbind(model.ABCC.site.results,p.adjust(coef(summary(model.ABCC.site))[,4],method="fdr"))

model.2mm.site<-glm(
  !gframes_0.2_375 ~ sex + household.income + p.edu + race_ethnicity.factor + 
    ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z 
    + nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + 
    pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z + bmiAgeZ + 
    site_id_l,
  data=df,
  family="binomial")
model.2mm.site.results<-cbind(confint(model.2mm.site,level=.95),model.2mm.site$coefficients)[,c(1,3,2)]
model.2mm.site.results<-cbind(model.2mm.site.results,p.adjust(coef(summary(model.2mm.site))[,4],method="fdr"))

model.QC2.site<-glm(
  !ABCD_rsfmri_QC2 ~ sex + household.income + p.edu + race_ethnicity.factor + 
    ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z 
    + nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + 
    pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z + bmiAgeZ + 
    site_id_l,
  data=df,
  family="binomial")
model.QC2.site.results<-cbind(confint(model.QC2.site,level=.95),model.QC2.site$coefficients)[,c(1,3,2)]
model.QC2.site.results<-cbind(model.QC2.site.results,p.adjust(coef(summary(model.QC2.site))[,4],method="fdr"))

```

#### Figure 4: Missingness by site, inclusion criteria

```{r fig.cap="% Missing by site, inclusion criteria",fig.height=4,fig.width=10}
sitesummary <- df %>% group_by(site_id_l) %>%
  summarise(
    "ExcludedPerc.QC2" = mean(!ABCD_rsfmri_QC2),
    "ExcludedPerc.ABCC" = mean(!any_rest),
    "ExcludedPerc.2mm" = mean(!gframes_0.2_375),
    "ExcludedPerc.fastqc" = mean(!fastqcok)
  ) %>%
  arrange(site_id_l) %>%
  mutate(
    sitelabel = recode_factor(
      site_id_l,
      `site01` = "Los Angeles, CA (CHLA)",
      `site02` = "Boulder, CO",
      `site03` = "Miami, FL",
      `site04` = "Tulsa, OK",
      `site05` = "Columbia, SC",
      `site06` = "Portland, OR",
      `site07` = "Rochester, NY",
      `site08` = "Menlo Park, CA",
      `site09` = "Los Angeles, CA (UCLA)",
      `site10` = "San Diego, CA",
      `site11` = "Gainsville, FL",
      `site12` = "Baltimore, MD",
      `site13` = "Ann Arbor, MI",
      `site14` = "Minneapolis, MN",
      `site15` = "Pittsburgh, Pa",
      `site16` = "Salt Lake City, UT",
      `site17` = "Burlington, VT",
      `site18` = "Milwaukee, WI",
      `site19` = "Richmond, VA",
      `site20` = "St. Louis, MO",
      `site21` = "New Haven, CT",
      `site22` = "New York, NY"
    )
  )

sitesummary2 <- sitesummary %>%
  mutate(sitelabel = fct_reorder(sitelabel, ExcludedPerc.QC2)) %>%
  pivot_longer(
    cols = starts_with("ExcludedPerc"),
    names_to = "sample",
    names_prefix = "ExcludedPerc\\.",
    values_to = "Percent_Missing"
  ) %>%
  mutate(sample = factor(
    sample,
    levels = c("fastqc",
               "QC2",
               "ABCC",
               "2mm"),
    labels = c("Current FastQC",
               "DAIC inclusion",
               "ABCC",
               "ABCC <.2mm FD")
  ))

sensplot1<-ggplot(sitesummary2, 
       aes(x=sitelabel,y=Percent_Missing,fill=sample)) +
  geom_col(position="dodge") +
  theme(axis.title.x=element_blank(),
        legend.title= element_blank()) +
  ylab("% Excluded") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  scale_fill_viridis(discrete=TRUE) +
  ggtitle("% Missing by site, inclusion criteria")

```

```{r fig.cap="N Missing in ABCC by site, race/ethnicity",fig.height=4,fig.width=10}
sitesummary3 <- df %>% group_by(site_id_l,race_ethnicity.factor) %>%
  summarise(
    "ExcludedN" = sum(!any_rest),
    "TotalN" = n()) %>%
  mutate(
    sitelabel = recode_factor(
      site_id_l,
      `site01` = "Los Angeles, CA (CHLA)",
      `site02` = "Boulder, CO",
      `site03` = "Miami, FL",
      `site04` = "Tulsa, OK",
      `site05` = "Columbia, SC",
      `site06` = "Portland, OR",
      `site07` = "Rochester, NY",
      `site08` = "Menlo Park, CA",
      `site09` = "Los Angeles, CA (UCLA)",
      `site10` = "San Diego, CA",
      `site11` = "Gainsville, FL",
      `site12` = "Baltimore, MD",
      `site13` = "Ann Arbor, MI",
      `site14` = "Minneapolis, MN",
      `site15` = "Pittsburgh, Pa",
      `site16` = "Salt Lake City, UT",
      `site17` = "Burlington, VT",
      `site18` = "Milwaukee, WI",
      `site19` = "Richmond, VA",
      `site20` = "St. Louis, MO",
      `site21` = "New Haven, CT",
      `site22` = "New York, NY"
    )) %>% 
  mutate(sitelabel = factor(sitelabel,levels=levels(sitesummary2$sitelabel)))

sensplot2<-ggplot(sitesummary3,  
       aes(x=sitelabel,y=ExcludedN,fill=race_ethnicity.factor)) +
  geom_col(position="stack") +
  theme(axis.title.x=element_blank(),
        legend.title=element_blank()) +
  ylab("N Excluded") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  scale_fill_viridis(discrete=TRUE) +
  ggtitle("N Missing in ABCC by site, race/ethnicity")

```

```{r fig.cap="N in ABCC by site, race/ethnicity",fig.height=4,fig.width=10}
sensplot3<-ggplot(sitesummary3,  
       aes(x=sitelabel,y=TotalN,fill=race_ethnicity.factor)) +
  geom_col(position="stack") +
  theme(axis.title.x=element_blank(),
        legend.title=element_blank()) +
  ylab("N") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  scale_fill_viridis(discrete=TRUE) +
  ggtitle("N included in ABCC by site, race/ethnicity")

```


```{r}
ggsave("Manuscript/Figures/sensplot.svg",(sensplot1 / sensplot2 / sensplot3),height=9,width=7.5)
```

## Trends Across Conditions
See 'Supplementary Results' for discussion of the formal model.

```{r}
# A 'long' format dataframe with thresholds within participants is used for these
# plots

pmisssum <- df %>% summarise(across(c(any_rest,
                                      ends_with("_375")),
                                    ~mean(!.))) %>% 
  unlist()

dflong <- df %>%
  pivot_longer(cols=c(any_rest,gframes_0.01_375:gframes_0.5_375),
                              names_to="threshold",
                              values_to="missing") %>%
  mutate(missing=!missing)

dflong$pmiss<-pmisssum[dflong$threshold]
```

### Condition trend plots plotting (Figure 5)

```{r}
# These functions draw plots with predicted probability of missingness 
# (by group) - probability of missingness in the whole sample.

# What ticks do we want for these plot?
xticks.mm<-c(.5,.45,.4,.35,.3,.25,.2,.15,.1,.05)
xticks.pmiss<-pmisssum[c("any_rest",paste0("gframes_",xticks.mm,"_375"))]
xticks.perc<-round(xticks.pmiss*100,0)
xticks.labela<-c("C",paste0(xticks.mm,"mm"))
xticks.label<-paste0(xticks.labela,"\n(",xticks.perc,"%)")
xticks.label[c(2:7)]<-""

detrend_catemplot <- function(x, label) {
  quosure <- quo(!!sym(x))
  #The probability (average) without any cross control.
  mdf <- dflong %>%
    select(c(!!quosure, pmiss, missing)) %>%
    group_by(!!quosure, pmiss) %>%
    filter(n() >= 50) %>% # Remove cases with n<50. Otherwise they are very noisy.
    summarise(avg = mean(missing)) %>%
    mutate(ydt = avg - pmiss,
           yvar = avg)
  names(mdf)[1] <- "tvar"
  ggplot(mdf, aes(x = pmiss,y = ydt,color = tvar,fill = tvar)) +
    geom_point() +
    scale_color_viridis(name = x,
                        discrete = TRUE,
                        na.value = "gray") +
    scale_fill_viridis(name = x,
                       discrete = TRUE,
                       na.value = "gray") +
    labs(title = paste("De-trended Mean Missingness by", label)) +
    scale_x_continuous(breaks = xticks.pmiss, labels = xticks.label) +
    theme(
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      legend.title = element_blank(),
      legend.text = element_text(size = 10)
    )
}

# 3 As above, but for continuous variables.
detrend_contemplot<-function(x,label) {
  quosure<-quo(!!sym(x))
  #Add the probability (average) without any cross control.
  mdf<-dflong %>%
    select(c(!!quosure,pmiss,missing)) %>%
    mutate(quantile=ntile(!!quosure,5)) %>% 
    group_by(quantile,pmiss) %>%
    summarise(avg=mean(missing)) %>%
    mutate(ydt=avg-pmiss,
           Quantile=as.factor(quantile))
  ggplot(mdf,aes(x=pmiss,y=ydt,color=Quantile)) +
       geom_point() +
       scale_color_viridis(discrete=TRUE) +
       labs(title=paste("De-Trended Mean Missingness by",label)) +
    scale_x_continuous(breaks=xticks.pmiss,labels = xticks.label) +
    theme(axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          legend.text=element_text(size=10))
}
```

```{r}
# Sub-Plots:
# Categorical:
h2p1<-detrend_catemplot("sex","Sex")
h2p2<-detrend_catemplot("ksads_factor","Trauma Count")
h2p3<-detrend_catemplot("race_ethnicity.factor","Census Race/Ethnicity")
h2p4<-detrend_catemplot("household.income","Household Income")
h2p5<-detrend_catemplot("p.edu","Highest Parental Education")
h2p6<-detrend_catemplot("pds_category","Pubertal Status")

# Continuous:
h2plot.adi<-detrend_contemplot("adi.z","ADI")
h2plot.coi<-detrend_contemplot("coi.z","COI")
h2plot.flank<-detrend_contemplot("nihtbx_flanker_agecorrected.z","NIHTB Flanker Score")
h2plot.cryst<-detrend_contemplot("nihtbx_cryst_agecorrected.z","NIHTB Crystalized")
h2plot.ntot<-detrend_contemplot("nihtbx_totalcomp_agecorrected.z","NIHTB Total")
h2plot.wisc<-detrend_contemplot("pea_wiscv_tss.z","Wisc V Matrix")
h2plot.pfac<-detrend_contemplot("pfactor.z","P-factor")
h2plot.int<-detrend_contemplot("INT.z","Internalizing")
h2plot.ext<-detrend_contemplot("EXT.z","Externalizing")
h2plot.age<-detrend_contemplot("interview_age.z","Age")
h2plot.bmi<-detrend_contemplot("bmiAgeZ","BMI")

# A few outstanding effects are saved to a plot for the manuscript:
svg(filename="Manuscript/Figures/h2catfig.svg",height=9,width=7.5,family="Times New Roman")
h2p4 / h2p5 / h2plot.ntot / h2plot.bmi
grid::grid.draw(grid::textGrob("Proportion of Participants Excluded − Total Proportion Excluded",x=.01,rot=90,gp = grid::gpar(fontfamily = "Times New Roman")))
grid::grid.draw(grid::textGrob("Motion Threshold (Proportion of Sample Missing)",y=.01,gp = grid::gpar(fontfamily = "Times New Roman")))
dev.off()
```


## QCFC Figures (Figure 6)

```{r}
# Get the Glasser Distances
files=c("ABCC_download/GlasserDistances/glasserdistances.txt",
        list.files("ABCC_download/",pattern="QCFC.*csv",full.names = TRUE))

#A list of vectors:
QCFCvals<-lapply(files,scan,sep=",")

# The distance matrix only has cortical (as opposed to subcortical distances, so 
# we trim the QC-FC values to those dimensions. All of these matrices are 
# symmetrical across the diagonal, so we can also omit the diagonal and lower 
# triangle.

tdim=sqrt(length(QCFCvals[[1]]))
QCFCtrimvals <- lapply(QCFCvals,\(x) {
  m=matrix(x,ncol=sqrt(length(x)),byrow=TRUE)
  m2=m[1:tdim,1:tdim]
  m2[lower.tri(m2,diag = TRUE)] <- NA
  na.omit(c(m2))
  })

QCFCdf<-as.data.frame(reduce(QCFCtrimvals,cbind))
names(QCFCdf)<-c("distance","<.1mm","<.2mm","<.3mm","<.4mm","<.5mm","No Scrubbing")
QCFCdflong <- QCFCdf %>% pivot_longer(cols=-distance,
                                      names_to="threshold",
                                      values_to="QCFC")

# Calculate Slopes
QCFCdfz <- QCFCdf %>% 
  mutate(across(.fns=scale))

annotext<-function(x) {
  m<-lm(QCFCdfz$distance ~ QCFCdfz[,x])
  ci<-confint(m,level=.80)
  spec="%.2f"
  paste0("β = ",
         sprintf(spec,m$coefficients[2]),
         " 99% CI [",
         sprintf(spec,ci[2,1]),
         " ",
         sprintf(spec,ci[2,2]),
         "]")
}

annot<-data.frame(threshold=unique(QCFCdflong$threshold),
                 text=sapply(unique(QCFCdflong$threshold),annotext))
annot$text<-gsub("0\\.", ".", annot$text)
annot$distance=mean(range(QCFCdflong$distance))
annot$QCFC=.1
```

 
```{r fig.cap="Hexagonal binned density plots of the correlation between participants' functional connectivity in each pair of regions in the HCP 2016 cortical atlas and framewise displacement, plotted against the average euclidean distance between said regions. Data from all ABCC participants is included (n=9,600)",fig.height=6.75,fig.width=10,cache.extra=annot}
ggsave("Manuscript/Figures/qcfc.svg",
ggplot(QCFCdflong,aes(x=distance,y=QCFC)) +
  geom_hex(aes(color=..count..),bins=40) +
  labs(x="ROI Distance (mm)",
       y="QC-FC") +
  theme(legend.position="none") +
  scale_fill_gradient(low="white",high="black") +
  scale_colour_gradient(low="white",high="black") +
  geom_smooth(method="lm",color="red") +
  facet_wrap(~threshold) +
  geom_text(data=annot,mapping=aes(label=text,family="Times New Roman"),parse=FALSE),
height=5.5,width=7.5,)
```

## Multiply at Risk Cell Counts

```{r}
subdf1 <- df %>% 
  filter(race_ethnicity.factor!="White",
         pfactor.z>=1.5)

subtable1<-data.frame(
  "F"=nrow(subdf1),
  "T"=sum(subdf1$ABCD_rsfmri_QC1),
  "C"=sum(subdf1$any_rest),
  ".5"=sum(subdf1$gframes_0.5_375),
  ".4"=sum(subdf1$gframes_0.4_375),
  ".3"=sum(subdf1$gframes_0.3_375),
  "R"=sum(subdf1$ABCD_rsfmri_QC2),
  ".2"=sum(subdf1$gframes_0.2_375),
  ".1"=sum(subdf1$gframes_0.1_375)
  ) %>% 
  as_hux() %>% 
  set_header_rows(1,TRUE) %>% 
  set_caption("Non-white (census) with psychopathology at z >= 1.5")


subtable1[1,]<-gsub("X\\.","\\.",subtable1[1,])

subdf2 <- df %>% 
  filter(nihtbx_totalcomp_agecorrected.z<=-1.5,
         sex=="M")

subtable2<-data.frame(
  "F"=nrow(subdf2),
  "T"=sum(subdf2$ABCD_rsfmri_QC1),
  "C"=sum(subdf2$any_rest),
  ".5"=sum(subdf2$gframes_0.5_375),
  ".4"=sum(subdf2$gframes_0.4_375),
  ".3"=sum(subdf2$gframes_0.3_375),
  "R"=sum(subdf2$ABCD_rsfmri_QC2),
  ".2"=sum(subdf2$gframes_0.2_375),
  ".1"=sum(subdf2$gframes_0.1_375)
  ) %>% 
  as_hux() %>% 
  set_header_rows(1,TRUE) %>% 
  set_caption("Male participants with NIH toolbox total scores of z <= -1.5")

subtable2[1,]<-gsub("X\\.","\\.",subtable2[1,])
```

...of the `r as.numeric(subtable1[2,1])` participants in ABCD who identified as non-white and who had a p-factor score of greater than 1.5, `r as.numeric(subtable1[2,1])-as.numeric(subtable1[2,7])` (`r (as.numeric(subtable1[2,1])-as.numeric(subtable1[2,7]))/as.numeric(subtable1[2,1])`%) were flagged for inclusion in resting state analyses by the DAIRC (vs `r ((nrow(df)-as.numeric(subtable1[2,1])) - (sum(df$ABCD_rsfmri_QC2)-as.numeric(subtable1[2,7])))/(nrow(df)-as.numeric(subtable1[2,1]))`% in the rest of the sample); of the `r as.numeric(subtable2[2,1])` ABCD participants assigned male at birth with NIH toolbox scores of z <=-1.5, `r as.numeric(subtable2[2,1])-as.numeric(subtable2[2,7])` (`r (as.numeric(subtable2[2,1])-as.numeric(subtable2[2,7]))/as.numeric(subtable2[2,1])`%) were not recommended for inclusion by DAIRC (vs. `r ((nrow(df)-as.numeric(subtable2[2,1])) - (sum(df$ABCD_rsfmri_QC2)-as.numeric(subtable2[2,7])))/(nrow(df)-as.numeric(subtable2[2,1]))`% in the rest of the sample).

## Save Tables

```{r}
openxlsx::saveWorkbook(tables.xlsx,"Manuscript/Tables/tables.xlsx",overwrite=TRUE)
```

```{=latex}
\fi
```

# Supplementary Results

## F-tests for discrete variable-Motion associations

In the manuscript, F tests associated with the discrete variables tested are omitted for brevity. These are printed in Tables 1-2.

```{r}
discOut %>% 
  filter(IV %in% c("filtered_fd_0.1","filtered_fd_0.2","filtered_fd_0.3")) %>% 
  select(DV:MODEL_P) %>% 
  distinct() %>% 
  as_hux() %>% 
  insert_column(c("Threshold",rep(c(".1mm",".2mm",".3mm"),each=6))) %>% 
  set_caption("F tests for relation of discrete DVs with FD after scrubbing, by threshold (pt. 1)")
```

```{r}
discOut %>% 
  filter(IV %in% c("filtered_fd_0.4","filtered_fd_0.5")) %>% 
  select(DV:MODEL_P) %>% 
  distinct() %>% 
  as_hux() %>% 
  insert_column(c("Threshold",rep(c(".4mm",".5mm"),each=6))) %>% 
  set_caption("F tests for relation of discrete DVs with FD after scrubbing, by threshold (pt. 2)")
```

## Multiply at Risk Cell Counts

Count of participants with multiple risk factors who were excluded (by condition) appear in Table 3-4.

```{r}
subtable1
```


```{r}
subtable2
```


## Categorical Variable Table by Condition

See Table 5.

```{r}
catvars<-c("sex",
             "household.income",
             "p.edu",
             "race_ethnicity.factor",
             "ksads_factor",
             "pds_category")

catTableAtThresh <- function(dataorig,
                             boolean,
                             base = NULL,
                             vars = catvars) {
  n <- sum(boolean)
  tl <- list(cbind(n, n * 100 / 11876))
  pdivisor <- n
  data <- dataorig[boolean, ]
  row.names(tl[[1]]) <- "Total"
  for (i in vars) {
    st <-
      cbind(table(data[, i], useNA = "always"), (table(data[, i], useNA = "always") *
                                                   100) / pdivisor)
    tl[[length(tl) + 1]] <- st
  }
  t <- reduce(tl, rbind)
  if (is.null(base)) {
    t
  } else {
    cbind(t, t[, 2] - base[, 2])
  }
}

CatVar375Table <- cbind(
  catTableAtThresh(df, rep(TRUE,nrow(df))),
  catTableAtThresh(df, df$ABCD_rsfmri_QC1),
  catTableAtThresh(df, df$any_rest),
  catTableAtThresh(df, df$gframes_0.5_375),
  catTableAtThresh(df, df$gframes_0.4_375),
  catTableAtThresh(df, df$gframes_0.3_375),
  catTableAtThresh(df, df$ABCD_rsfmri_QC2),
  catTableAtThresh(df, df$gframes_0.2_375),
  catTableAtThresh(df, df$gframes_0.1_375)
)

#Try to draw as a huxtable
rownames(CatVar375Table)<-gsub("\\$","\\\\$",rownames(CatVar375Table))
CatVar375Hux<-as_hux(CatVar375Table) %>%
  theme_basic() %>%
  insert_row(value=c("n","\\%",rep(c("n","\\%"),8))) %>%
  insert_row("Full","",
             "QC1","",
             "ABCC","",
             ".5","",
             ".4","",
             ".3mm","",
             "QC2","",
             ".2mm","",
             ".1mm","") %>%
  merge_cells(1,1:2) %>%
  merge_cells(1,3:4) %>%
  merge_cells(1,5:6) %>%
  merge_cells(1,7:8) %>%
  merge_cells(1,9:10) %>%
  merge_cells(1,11:12) %>%
  merge_cells(1,13:14) %>%
  merge_cells(1,15:16) %>%
  merge_cells(1,17:18) %>% 
  insert_column(value=c("","",rownames(CatVar375Table) %>% replace_na("Missing"))) %>%
  insert_column(value=c("","","Total","Sex","","",
                        "Income","","","","","","",
                        "Parent Ed.","","","","","",
                        "Race/Ethnicity","","","","","",
                        "Trauma Count","","","",
                        "Puberty","","","","","")) %>%
  set_caption("Categorical Values at Each Level of Stringency (Subjects excluded with < 375 Frames), Pt 1") %>%
  set_escape_contents(FALSE)  %>%
  set_font_size(8) %>%
  set_number_format(3:nrow(.),3+0:7*2,value=fmt_pretty()) %>%
  set_number_format(3:nrow(.),4+0:7*2,value="%.2g") %>%
  set_all_padding(1)

CatVar375Hux
```

## Missingness in Behavioral Data

Table 6 shows missingness counts in non-imaging variables with more than 50 missing cases.

```{r}
df %>% 
  select(c(interview_age:household.income,p.edu,race_ethnicity.factor:site_id_l)) %>%
  rename(c("Child Opportunity Index"="coi","Household Income"="household.income","Area Disadvantage Index"="adi","NIH Toolbox Total"="nihtbx_totalcomp_agecorrected","NIH Toolbox Crystalized"="nihtbx_cryst_agecorrected","WISC V"="pea_wiscv_tss","NIH Toolbox Flanker"="nihtbx_flanker_agecorrected","Pubertal Status"="pds_category")) %>% 
  summarise_all(~sum(is.na(.))) %>% 
  pivot_longer(everything()) %>% 
  filter(value>50) %>% 
  mutate(`% missing`=(value/nrow(df))*100) %>% 
  arrange(desc(value)) %>% 
  rename(c("Variable"="name","n Missing"="value")) %>% as_hux() %>% 
  set_header_rows(1,TRUE) %>% 
  set_caption("Behavioral and Demographic variables with >50 missing values")
```

## Adjusted Models -- Forest Plot

Figure 1-2 depict effects from the adjusted/condition models.

```{r}
MFformat<-\(m) {
  stars<-sdlabFunctions::starPs(m[,4])
  paste0(ORformat(m[,2]),
         stars,
         "\n[",ORformat(m[,1]),"–",ORformat(m[,3]),"]")
}

allmodelterms<-c(
    "(Intercept)",
    "sexM",
    "household.incomeheader",
    "household.income$0 to $25k",
    "household.income$25k to $50k",
    "household.income$50k to $75k",
    "household.income$75k to $100k",
    "household.incomeOver $200k",
    "p.eduheader",
    "p.edu< HS",
    "p.eduGraduate Degree",
    "p.eduHS Graduate",
    "p.eduSome College",
    "race_ethnicityheader",
    "race_ethnicity.factorAsian",
    "race_ethnicity.factorBlack",
    "race_ethnicity.factorHispanic",
    "race_ethnicity.factorOther",
    "ksadsheader",
    "ksads_factor>2",
    "ksads_factor1",
    "pdsheader",
    "pds_categoryearly puberty",
    "pds_categorylate puberty",
    "pds_categorymid puberty",
    "pds_categorypost pubertal",
    "adi.z",
    "coi.z",
    "nihtbx_flanker_agecorrected.z",
    "nihtbx_cryst_agecorrected.z",
    "nihtbx_totalcomp_agecorrected.z",
    "pea_wiscv_tss.z",
    "pfactor.z",
    "INT.z",
    "EXT.z",
    "interview_age.z",
    "bmiAgeZ")

alllevelsggplot<-c("Intercept",
      "Sex (Male)",
      "**Household Income**",
      "  $0-$25k",
      "  $25-$50k",
      "  $50-$75k",
      "  $75-$100k",
      "  &gt;$200k",
      "**Highest Parental Education**",
      "  &lt;High School",
      "  HS Grad.",
      "  Some College",
      "  Graduate",
      "**Census Race/Ethnicity**",
      "  Black",
      "  Hispanic",
      "  Asian",
      "  Other",
      "**Trauma Count**",
      "  1 Trauma",
      "  &gt;=2 Trauma",
      "**Pubertal Status**",
      "  Early Puberty",
      "  Mid Puberty",
      "  Late Puberty",
      "  Post Pubertal",
      "Area Disadvantage",
      "Child Opportunity",
      "NIHTB Flanker",
      "NIHTB Crystalized",
      "NIHTB Total",
      "WISC V Matrix",
      "Psychopathology",
      "Internalizing",
      "Externalizing",
      "Age",
      "BMI"
      )

modeltermsA<-allmodelterms[1:18]
modeltermLabelsA<-alllevelsggplot[1:18]
modeltermsB<-allmodelterms[19:length(allmodelterms)]
modeltermLabelsB<-alllevelsggplot[19:length(allmodelterms)]

forestdf <- rbind(
  model.QC1.results %>% data.frame() %>% rownames_to_column(),
  model.ABCC.results %>% data.frame() %>% rownames_to_column(),
  model.5mm.results %>% data.frame() %>% rownames_to_column(),
  model.4mm.results %>% data.frame() %>% rownames_to_column(),
  model.3mm.results %>% data.frame() %>% rownames_to_column(),
  model.QC2.results %>% data.frame() %>% rownames_to_column(),
  model.2mm.results %>% data.frame() %>% rownames_to_column(),
  model.1mm.results %>% data.frame() %>% rownames_to_column()
) %>% mutate(threshold=factor(rep(c("T","C","5","4","3","R","2","1"),each=nrow(model.QC1.results)))) %>% 
  rename_with(~ c("term","lowCI","OR","highCI","p","threshold")) %>% 
  mutate(across(lowCI:highCI,exp)) %>% 
  add_row(term="household.incomeheader") %>% 
  add_row(term="p.eduheader") %>% 
  add_row(term="ksadsheader") %>% 
  add_row(term="pdsheader") %>% 
  add_row(term="race_ethnicityheader") %>% 
  mutate(threshold=factor(threshold))

maxsigCI<-max(forestdf[forestdf$lowCI>1,"highCI"],na.rm=TRUE)
forestdf[forestdf$highCI>maxsigCI & !is.na(forestdf$highCI),"highCI"]<-maxsigCI


forestdfA<- forestdf %>% filter(term %in% modeltermsA) %>% 
  mutate(term=factor(term,
                     levels=modeltermsA,
                     labels=modeltermLabelsA))
forestdfB<- forestdf %>% filter(term %in% modeltermsB) %>% 
  mutate(term=factor(term,
                     levels=modeltermsB,
                     labels=modeltermLabelsB))

dodge<-.8
```

```{r fig.cap="Odds ratios for missingness by threshold -- Adjusted Models (part 1)",fig.height=6.75,fig.width=9}
ggplot(forestdfA,aes(y=term,color=threshold)) + 
  geom_vline(lty=2,aes(xintercept=1),colour='black') +
  geom_point(aes(x=OR),position=ggstance::position_dodgev(height=dodge)) +
  geom_linerange(aes(xmin=lowCI,xmax=highCI,y=term),position=ggstance::position_dodgev(height=dodge)) +
  xlim(0,maxsigCI) +
  geom_vline(lty=2,aes(xintercept=1),colour='black') +
  scale_y_discrete(drop=FALSE,limits=rev) +
  scale_color_discrete(limits=rev,drop=TRUE,na.translate = F) +
  theme(axis.text.y=element_markdown(),
        axis.title.y=element_blank()) +
  xlab("Odds Ratio of Missingness + 95% CI")
```

```{r fig.cap="Odds ratios for missingness by threshold -- Adjusted Models (part 2)",fig.height=6.75,fig.width=9}

ggplot(forestdfB,aes(y=term,color=threshold)) +
  geom_vline(lty=2,aes(xintercept=1),colour='black') +
  geom_point(aes(x=OR),position=ggstance::position_dodgev(height=dodge)) +
  geom_linerange(aes(xmin=lowCI,xmax=highCI,y=term),position=ggstance::position_dodgev(height=dodge)) +
  xlim(0,maxsigCI) +
  scale_y_discrete(drop=FALSE,limits=rev) +
  scale_color_discrete(limits=rev,drop=TRUE,na.translate = F) +
  theme(axis.text.y=element_markdown(),
        axis.title.y=element_blank()) +
  xlab("Odds Ratio of Missingness + 95% CI")
```

## Sensitivity to Site/Scanner

Percent Excluded by site is shown in table 7.

```{r}
sitesummary2 %>%  
  group_by(sample) %>% 
  filter(Percent_Missing == max(Percent_Missing)) %>%
  mutate(Percent_Missing = Percent_Missing*100) %>% 
  select(sitelabel:Percent_Missing) %>% 
  rename("Site"="sitelabel",
         "Condition"="sample",
         "% Excluded"="Percent_Missing") %>% 
  as_hux() %>% 
  set_caption("Sites with Highest \\% Excluded, by Condition")
```

### Sensitivity to Site/Scanner Table

Table 8 shows fixed effects of a 'scanner type' variable in 3 of our 'adjusted' models both with and without control for site.

```{r}
MformatCI <- \(m) {
  stars <- sdlabFunctions::starPs(m[, 4])
  cbind(
    paste0(
      ORformat(m[, 2]),
      stars,
      " [",
      ORformat(m[, 1]),
      "–",
      ORformat(m[, 3]),
      "]"))
}

sitecoefs<-rbind(cbind(MformatCI(model.ABCC.scanner.results)[33:36,],
      MformatCI(model.QC2.scanner.results)[33:36,],
      MformatCI(model.2mm.scanner.results)[33:36,]),
      cbind(MformatCI(model.ABCC.scanner.site.results)[33:36,],
      MformatCI(model.QC2.scanner.site.results)[33:36,],
      MformatCI(model.2mm.scanner.site.results)[33:36,]))

as_huxtable(sitecoefs) %>%
  insert_row(c("ABCC", "QC2", ".2mm")) %>%
  insert_row(c("Without Site Control", "", "")) %>%
  merge_cells(1, 1:3) %>%
  #merge_cells(2, 1:3) %>%
  insert_row(c("With Site Control","",""),after = 6) %>% 
  merge_cells(7,1:3) %>% 
  insert_column(
    c(
      "",
      "Scanner (ref: Philips Achieva)",
      "GE Discovery MR750",
      "Philips Ingenia",
      "Siemens Prisma",
      "Siemens Prisma fit",
      "",
      "GE Discovery MR750",
      "Philips Ingenia",
      "Siemens Prisma",
      "Siemens Prisma fit"
    )
  ) %>%
  set_caption("OR of scanner type effect, with and without site control, in condition adjusted models [95\\% CI]. ***: p<.001") %>% 
  set_wrap(TRUE) %>% 
  set_width(1)
```

### Sensitivity to Site/Scanner Forest Plots

Figures 3-4 show forest plots of ORs with a significant (p<.05) model term in either the site-controlled or the site un-controlled adjusted model. They are here to visualize the effects of site control on the adjusted models.

```{r fig.cap="Significant ORs predicting ABCC missingness with and without site control"}
ABCC.compdf <- rbind(
  model.ABCC.site.results %>%
    as.data.frame() %>%
    rownames_to_column("term") %>%
    rename_with( ~ c("term", "lowCI", "OR", "highCI", "p")) %>%
    mutate(
      lowCI = replace_na(lowCI, min(lowCI, na.rm = TRUE)),
      highCI = replace_na(highCI, max(highCI, na.rm = TRUE)),
      sig = p < .05,
      model = "Site Control"
    ) %>%
    mutate(across(lowCI:highCI, exp)),
  model.ABCC.results %>%
    as.data.frame() %>%
    rownames_to_column("term") %>%
    rename_with( ~ c("term", "lowCI", "OR", "highCI", "p")) %>%
    mutate(
      lowCI = replace_na(lowCI, min(lowCI, na.rm = TRUE)),
      highCI = replace_na(highCI, max(highCI, na.rm = TRUE)),
      sig = p < .05,
      model = "No Control"
    ) %>%
    mutate(across(lowCI:highCI, exp))
) %>%
  mutate(model = as.factor(model),
         alphaval=case_when(sig ~ 1,
                            !sig ~ .5))


#terms where one model coefficient was sig
sigterms <-
  (ABCC.compdf %>% group_by(term) %>% summarise(anysig = sum(sig) != 0) %>% filter(anysig))$term

ABCC.compdf<-ABCC.compdf %>% mutate(alphaval=factor(alphaval,levels=c(.5,1),labels=c("p>.05","p<.05")))

test<-ggplot(ABCC.compdf %>% filter(term %in% sigterms),
       aes(x = term, color = model, alpha = alphaval)) +
  geom_point(aes(y = OR), position = position_dodge(.2)) +
  geom_linerange(aes(ymin = lowCI, ymax = highCI, x = term),
                 position = position_dodge(.2)) +
  ylim(-4, 4) +
  geom_hline(lty = 2, aes(yintercept = 1), colour = 'black') +
  coord_flip() + theme(legend.title = element_blank())
```


```{r fig.cap="Significant ORs predicting DAIRC Recommended missingness with and without site control"}
QC2.compdf <- rbind(
  model.QC2.site.results %>%
    as.data.frame() %>%
    rownames_to_column("term") %>%
    rename_with( ~ c("term", "lowCI", "OR", "highCI", "p")) %>%
    mutate(
      lowCI = replace_na(lowCI, min(lowCI, na.rm = TRUE)),
      highCI = replace_na(highCI, max(highCI, na.rm = TRUE)),
      sig = p < .05,
      model = "Site Control"
    ) %>%
    mutate(across(lowCI:highCI, exp)),
  model.QC2.results %>%
    as.data.frame() %>%
    rownames_to_column("term") %>%
    rename_with( ~ c("term", "lowCI", "OR", "highCI", "p")) %>%
    mutate(
      lowCI = replace_na(lowCI, min(lowCI, na.rm = TRUE)),
      highCI = replace_na(highCI, max(highCI, na.rm = TRUE)),
      sig = p < .05,
      model = "No Control"
    ) %>%
    mutate(across(lowCI:highCI, exp))
) %>%
  mutate(model = as.factor(model),
         alphaval=case_when(sig ~ 1,
                            !sig ~ .5))

#terms where one model coefficient was sig
sigterms<-(QC2.compdf %>% group_by(term) %>% summarise(anysig=sum(sig)!=0) %>% filter(anysig))$term

QC2.compdf<-QC2.compdf %>% mutate(alphaval=factor(alphaval,levels=c(.5,1),labels=c("p>.05","p<.05")))

ggplot(QC2.compdf %>% filter(term %in% sigterms),
       aes(x = term, color = model, alpha = alphaval)) +
  geom_point(aes(y = OR), position = position_dodge(.2)) +
  geom_linerange(aes(ymin = lowCI, ymax = highCI, x = term),
                 position = position_dodge(.2)) +
  ylim(-4, 4) +
  geom_hline(lty = 2, aes(yintercept = 1), colour = 'black') +
  coord_flip() + theme(legend.title = element_blank())

```

```{r fig.cap="Significant ORs predicting .2mm missingness with and without site control"}
twomm.compdf <- rbind(
  model.2mm.site.results %>%
    as.data.frame() %>%
    rownames_to_column("term") %>%
    rename_with( ~ c("term", "lowCI", "OR", "highCI", "p")) %>%
    mutate(
      lowCI = replace_na(lowCI, min(lowCI, na.rm = TRUE)),
      highCI = replace_na(highCI, max(highCI, na.rm = TRUE)),
      sig = p < .05,
      model = "Site Control"
    ) %>%
    mutate(across(lowCI:highCI, exp)),
  model.2mm.results %>%
    as.data.frame() %>%
    rownames_to_column("term") %>%
    rename_with( ~ c("term", "lowCI", "OR", "highCI", "p")) %>%
    mutate(
      lowCI = replace_na(lowCI, min(lowCI, na.rm = TRUE)),
      highCI = replace_na(highCI, max(highCI, na.rm = TRUE)),
      sig = p < .05,
      model = "No Control"
    ) %>%
    mutate(across(lowCI:highCI, exp))
) %>%
  mutate(model = as.factor(model),
         alphaval=case_when(sig ~ 1,
                            !sig ~ .5))


#terms where one model coefficient was sig
sigterms <-
  (twomm.compdf %>% group_by(term) %>% summarise(anysig = sum(sig) != 0) %>% filter(anysig))$term

twomm.compdf<-twomm.compdf %>% mutate(alphaval=factor(alphaval,levels=c(.5,1),labels=c("p>.05","p<.05")))

ggplot(twomm.compdf %>% filter(term %in% sigterms),
       aes(x = term, color = model, alpha = alphaval)) +
  geom_point(aes(y = OR), position = position_dodge(.2)) +
  geom_linerange(aes(ymin = lowCI, ymax = highCI, x = term),
                 position = position_dodge(.2)) +
  ylim(-4, 4) +
  geom_hline(lty = 2, aes(yintercept = 1), colour = 'black') +
  coord_flip() + theme(legend.title = element_blank())

```


## Current Fast Track QC vs DAIRC recommendations

We state in the text that the currently published fastqc is non-overlapping with DAIRC inclusion recommendations. This table illustrates that non-overlap.

The variable 'fastqcok' is TRUE for participants who have at least one T1, rs-fMRI, and field map image marked useable in the current (Last modified 09/09/2019) abcd_fastqc01.csv file. These recommendations are non overlapping with the tabular data list as well as DAIRC recommendations:

```{r}
table(df$fastqcok,df$ABCD_rsfmri_QC1,dnn=c("FastQC","Tabulated"))

table(df$fastqcok,df$ABCD_rsfmri_QC2,dnn=c("FastQC","DAIRC"))
```

## Modeling Trends Across Conditions (H2)

This model specifically looks at changes associated with motion threshold choice in the ABCC data. In the pre-registration, we originally proposed a mixed effects logistic model where each participant had a case for each motion threshold, and the percentage of data missing from each threshold was used as a within-subject variable. In simulation, we discovered a number of problems with this approach:

1. The proposed mixed effects logistic regression created very poor predictions and model fits in simulation, and often did not converge. A linear model of probability proved more stable and accurate and we determined to use that approach (a logistic model is also presented below, but it is similarly flawed).
2. We proposed that an interaction between a variable and the 'pmiss' variable would indicate that bias was worsening as more data was excluded. However, in simulating this approach we discovered that in the case that there was a bias but it did not worsen as more data was excluded, as, for example, if 2 males were excluded for every female, this would surface as a linear interaction between pmiss and sex in the model. Instead, a worsening bias would be indicated by an interaction between a variable and a polynomial of pmiss, which would indicate a curvilinear trajectory.

(notes from the simulation are available on osf)

An important remaining question from the simulation study was whether to include an intercept and main effects in the model. As, at pmiss=0, the probability of exclusion ought to be 0 for everyone, one could argue the intercept should be omitted. Model fit is compared between the two models in Table 9. The 'full' model has superior fit characteristics across indices. The GLM model, which is closer to what we originally proposed, does not converge and is not presented. 

```{r}
# h2 model with intercepts.
m.h2 <- lmer(
  missing ~ poly(pmiss, 2) +
    sex + sex:poly(pmiss, 2) +
    household.income + household.income:poly(pmiss, 2) +
    p.edu + p.edu:poly(pmiss, 2) +
    race_ethnicity.factor + race_ethnicity.factor:poly(pmiss, 2) +
    ksads_factor + ksads_factor:poly(pmiss, 2) +
    pds_category + pds_category:poly(pmiss, 2) +
    adi.z + adi.z:poly(pmiss, 2) +
    coi.z + coi.z:poly(pmiss, 2) +
    nihtbx_flanker_agecorrected.z + nihtbx_flanker_agecorrected.z:poly(pmiss, 2) +
    nihtbx_cryst_agecorrected.z + nihtbx_cryst_agecorrected.z:poly(pmiss, 2) +
    nihtbx_totalcomp_agecorrected.z + nihtbx_totalcomp_agecorrected.z:poly(pmiss, 2) +
    pea_wiscv_tss.z + pea_wiscv_tss.z:poly(pmiss, 2) +
    pfactor.z + pfactor.z:poly(pmiss, 2) +
    INT.z + INT.z:poly(pmiss, 2) +
    EXT.z + EXT.z:poly(pmiss, 2) +
    interview_age.z + interview_age.z:poly(pmiss, 2) +
    bmiAgeZ + bmiAgeZ:poly(pmiss, 2) +
    (pmiss | subjectkey),
  data = dflong
)

# h2 model with intercepts removed
m.h2.stripped <- lmer(
  missing ~ pmiss + poly(pmiss, 2) +
    sex:poly(pmiss,2) +
    household.income:poly(pmiss,2) +
    p.edu:poly(pmiss,2) +
    race_ethnicity.factor:poly(pmiss,2) +
    ksads_factor:poly(pmiss,2) +
    pds_category:poly(pmiss,2) +
    adi.z:poly(pmiss,2) +
    coi.z:poly(pmiss,2) +
    nihtbx_flanker_agecorrected.z:poly(pmiss,2) +
    nihtbx_cryst_agecorrected.z:poly(pmiss,2) +
    nihtbx_totalcomp_agecorrected.z:poly(pmiss,2) +
    pea_wiscv_tss.z:poly(pmiss,2) +
    pfactor.z:poly(pmiss,2) +
    INT.z:poly(pmiss,2) +
    EXT.z:poly(pmiss,2) +
    interview_age.z:poly(pmiss,2) +
    bmiAgeZ:poly(pmiss,2) +
    + 0 +
    (pmiss + 0 | subjectkey),
  data = dflong
)

# h2 model as a glm - this does not converge
# m.h2.glm<- glmer(
#   missing ~ poly(pmiss, 2) +
#     sex + sex:poly(pmiss, 2) +
#     household.income + household.income:poly(pmiss, 2) +
#     p.edu + p.edu:poly(pmiss, 2) +
#     race_ethnicity.factor + race_ethnicity.factor:poly(pmiss, 2) +
#     ksads_factor + ksads_factor:poly(pmiss, 2) +
#     pds_category + pds_category:poly(pmiss, 2) +
#     adi.z + adi.z:poly(pmiss, 2) +
#     coi.z + coi.z:poly(pmiss, 2) +
#     nihtbx_flanker_agecorrected.z + nihtbx_flanker_agecorrected.z:poly(pmiss, 2) +
#     nihtbx_cryst_agecorrected.z + nihtbx_cryst_agecorrected.z:poly(pmiss, 2) +
#     nihtbx_totalcomp_agecorrected.z + nihtbx_totalcomp_agecorrected.z:poly(pmiss, 2) +
#     pea_wiscv_tss.z + pea_wiscv_tss.z:poly(pmiss, 2) +
#     pfactor.z + pfactor.z:poly(pmiss, 2) +
#     INT.z + INT.z:poly(pmiss, 2) +
#     EXT.z + EXT.z:poly(pmiss, 2) +
#     interview_age.z + interview_age.z:poly(pmiss, 2) +
#     bmiAgeZ + bmiAgeZ:poly(pmiss, 2) +
#     (pmiss | subjectkey),
#   family="binomial",
#   data = dflong,
#   nAGQ=0,
#   control=glmerControl(optimizer="nloptwrap")
# )

performance::print_md(performance::compare_performance(m.h2,m.h2.stripped))
```


```{r}
h2sum<-summary(m.h2)
temp = capture.output(h2sum)
End   = grep("Fixed effects", temp)-1
print(unname(temp[0:End]))
```

See Table 10-11 for the fixed effects from the omnibus model.

```{r h2table}
pnames<-rownames(h2sum$coefficients)

h2table<-h2sum$coefficients %>% as.data.frame() %>%
  rownames_to_column(var = "Parameter") %>%
  left_join(parameters::ci(m.h2)) %>%
  mutate(star = sdlabFunctions::starPs(`Pr(>|t|)`)) %>%
  select(c(Parameter, Estimate, CI_low, CI_high,star)) %>%
  mutate(level=c(1:3,rep(1,31),rep(2:3,31)),
         basep=c(rep("",3),pnames[4:34],rep(pnames[4:34],each=2))) %>%
  pivot_wider(id_cols=basep,names_from=level,values_from = Estimate:star) %>%
  mutate(across(where(is.numeric),ORformat))

h2hux<-h2table[,c(1,2,5,8,11,3,6,9,12,4,7,10,13)] %>%
  as_hux(add_colnames=FALSE) %>%
  insert_row("","Intercept","","","","pmiss","","","","pmiss^2","","","") %>%
  merge_cells(1, 2:5) %>% merge_cells(1, 6:9) %>% merge_cells(1, 10:12) %>%
  insert_row("","Main Eff.","","","","Interaction","","","","Q.Interaction","","","",after=2) %>%
  merge_cells(3, 2:5) %>% merge_cells(3, 6:9) %>% merge_cells(3, 10:12) %>%
  insert_row("",rep(c("B","CI.l","CI.u","*"),3)) 

h2hux[,1] <- c(rep("",4),alllevels[-1]) 

h2hux <- h2hux %>% insert_row(
    "Household Income (ref: $100-$200k)",
    after = 6,
    colspan = 9,
    fill = ""
  ) %>%
  insert_row(
    "Highest Parental Education (ref: College Degree)",
    after = 11,
    colspan = 9,
    fill = ""
  ) %>%
  insert_row(
    "Census Race/Ethnicity (ref: White)",
    after = 13+3,
    colspan = 9,
    fill = ""
  ) %>%
  insert_row(
    "KSADS Trauma Count (ref: 0 Exposures)",
    after = 18+3,
    colspan = 9,
    fill = ""
  ) %>%
  insert_row(
    "Pubertal Status (ref: pre-pubertal)",
    after = 21+3,
    colspan = 9,
    fill = ""
  )

h2hux[c(1:4,5:24),] %>% set_caption("H2 / Omnibus model fixed effects, pt. 1")
```

```{r}
h2hux[c(1:4,25:nrow(h2hux)),] %>% set_caption("H2 / Omnibus model fixed effects, pt. 2")
```

### H2 Marginal Means plotting (Figure 5)

```{r}
# These functions are similar to the ones defined above which draw simple trensd
# with means. These versions also include model generated marginal means. They
# use the same axis descriptors defined above.

detrend_catemplot_model<-function(x,label,model=NULL) {
  quosure<-quo(!!sym(x))
  if(!is.null(model)) {
  lmean <- emmeans(model,
                   as.formula(paste("~",x,"| pmiss")),
                     "pmiss",
                     at = list(pmiss=xticks.pmiss,
                               z=levels(df %>% 
                                          group_by(!!quosure) %>%
                                          filter(n() >= 50) %>% 
                                          ungroup() %>% 
                                          select(!!quosure) %>% 
                                          unlist())),
                   rg.limit = 400000)

  plot.dat<-emmip(lmean,
                  as.formula(paste(x,"~ pmiss")),
                  CIs=TRUE,
                  plotit = FALSE)
  }
  #Add detrended prediction
  plot.dat$ydt<-plot.dat$yvar-plot.dat$pmiss
  #Add the probability (average) without any cross control.

  mdf<-dflong %>%
    select(c(!!quosure,pmiss,missing)) %>%
    group_by(!!quosure,pmiss) %>%
    filter(n() >= 50) %>% # Remove cases with n<50. Otherwise they are very noisy.
    summarise(avg=mean(missing)) %>%
    mutate(ydt=avg-pmiss,
           yvar=avg)
  names(mdf)[1]<-"tvar"
  
  ggplot(plot.dat,aes(x=pmiss,y=ydt,color=tvar,fill=tvar)) +
       geom_smooth(method="loess") +
       geom_point(data=mdf) +
       scale_color_viridis(name=x,discrete = TRUE,na.value="gray") +
       scale_fill_viridis(name=x,discrete= TRUE,na.value="gray") +
       labs(title=paste("De-trended Mean Missingness by",label)) +
    scale_x_continuous(breaks=xticks.pmiss,labels = xticks.label) +
    theme(axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          legend.title=element_blank(),
          legend.text=element_text(size=10))# +
    #geom_function(fun = \(x) (-6.349e+00-3.078e-01)*x - (8.929e-01+1.996e+01)*x^2 + 3.078e-01)
}

```

The poor fit of the omnibus model is shown in Figure 5, a plot with both model predicted marginal means and the average inclusion within each factor level and motion threshold (here, lines are the model marginal means and points are the averages from the data).

```{r,fig.cap="Marginal Means Plot of Race/Ethnicity on exclusion by condition (adjusted)",fig.height=3,fig.width=9}
detrend_catemplot_model("race_ethnicity.factor","Census Race/Ethnicity",m.h2)
```

Figure 6 shows a similar plot but in a bivariate model -- fit is much improved, indicating that distortions in the first plot are most likely due to interference from other variables. Regardless, H2 is generally not supported by these results. The descriptive data is probably more helpful.

```{r,fig.cap="Marginal Means Plot of Race/Ethnicity on exclusion by condition (bivariate)",fig.height=3,fig.width=9}
# One variable, mixed-effect model.
m.h2.raceethnicity <- lmer(
  missing ~ poly(pmiss, 2) +
    race_ethnicity.factor + race_ethnicity.factor:poly(pmiss, 2) +
    (pmiss | subjectkey),
  data = dflong
)

detrend_catemplot_model("race_ethnicity.factor",
                        "Census Race/Ethnicity",
                        m.h2.raceethnicity)
```

Figures 7-9 reproduce Manuscript figures 5 for all of the other demographic and behavioral variables (in groups of 4):

```{r,fig.cap="Mean Inclusion/Exclusion by Supplemental Variables and condition (part 1)",fig.height=6.75,fig.width=9}
h2p1 / h2p2 / h2p3 / h2p6
grid::grid.draw(grid::textGrob("Proportion of Participants Excluded − Sample Mean",x=.01,rot=90,gp = grid::gpar(fontfamily = "Times New Roman")))
grid::grid.draw(grid::textGrob("Motion Threshold / Proportion of Sample Missing",y=.01,gp = grid::gpar(fontfamily = "Times New Roman")))
```

```{r,fig.cap="Mean Inclusion/Exclusion by Supplemental Variables and Condition (part 2)",fig.height=6.75,fig.width=9}
h2plot.adi / h2plot.coi / h2plot.flank / h2plot.cryst
grid::grid.draw(grid::textGrob("Proportion of Participants Excluded − Sample Mean",x=.01,rot=90,gp = grid::gpar(fontfamily = "Times New Roman")))
grid::grid.draw(grid::textGrob("Motion Threshold / Proportion of Sample Missing",y=.01,gp = grid::gpar(fontfamily = "Times New Roman")))
```

```{r,fig.cap="Mean Inclusion/Exclusion by Supplemental Variables and Condition (part 3)",fig.height=6.75,fig.width=9}
h2plot.wisc / h2plot.pfac / h2plot.int / h2plot.ext / h2plot.age
grid::grid.draw(grid::textGrob("Proportion of Participants Excluded − Sample Mean",x=.01,rot=90,gp = grid::gpar(fontfamily = "Times New Roman")))
grid::grid.draw(grid::textGrob("Motion Threshold / Proportion of Sample Missing",y=.01,gp = grid::gpar(fontfamily = "Times New Roman")))
```

## Association of QC missingness with Propensity weighting.

Gard (2020) notes that analyses using propensity weighting can be biased when missing data is correlated with population weights. They presented data that association between missingness and population weights are small when considering structural and task-based brain data from ABCD. Here, we repeat these analyses considering rs-fMRI data in each condition.

To the best of our knowledge, Gard et al. used Welch's two-sample t-tests to examine differences in propensity weight between included and excluded groups, and we will do the same here. Results from these tests are shown in table 12.

```{r}
gard_weighting_test<-function(boolvar) {
  formulastring=paste("acs_raked_propensity ~",boolvar)
  res<-broom::tidy(t.test(as.formula(formulastring), data=df, na.action="na.fail", conf.level=0.95))  
  names(res)<-c("delta","Mexcluded","Mincluded","t","p","df","ci.low","ci.high","method","alternative")
  res %>% select(delta:ci.high)
}

weight_ttests<-reduce(lapply(bools[-1],gard_weighting_test),rbind)
weight_ttests$d<-weight_ttests$delta/sd(df$acs_raked_propensity)
as_hux(weight_ttests) %>% 
  insert_column(c("",levelsdf$Level[-1]),after=0) %>% 
  set_caption("Propensity weights of included vs. excluded participants by condition; t-test parameters")
```

## Association of Exclusion with Expanded Demographic Variables

Available information on household income and (especially) race/ethnicity was greatly simplified in the main analysis for the purpose of brevity and to facilitate comparison with existing literature. For the sake of completeness and inclusivity, we present more nuanced codings of these variables here.

### Household Income

Table 13 and 14 presents descriptives and a bivariate model for a SES variable inclusive of all income bins available in the ABCD dataset.


```{r}
#Reorder the factor in increasing order and relabel for descriptives.
df$household.income.full<-factor(df$household.income.full,
                                 levels=c("Less than $5,000",
                                          "$5,000 through $11,999", 
                                          "$12,000 through $15,999", 
                                          "$16,000 through $24,999",
                                          "$25,000 through $34,999", 
                                          "$35,000 through $49,999", 
                                          "$50,000 through $74,999", 
                                          "$75,000 through $99,999", 
                                          "$100,000 through $199,999", 
                                          "$200,000 and greater"),
                                 labels=c("Less than \\$5k", 
                                          "\\$5k through \\$11.9k", 
                                          "\\$12k through \\$15.9k", 
                                          "\\$16k through \\$24.9k",
                                          "\\$25k through \\$34.9k", 
                                          "\\$35k through \\$49.9k", 
                                          "\\$50k through \\$74.9k", 
                                          "\\$75k through \\$99.9k",
                                          "\\$100k through \\$199.9k", 
                                          "\\$200k and greater"))

FullIncomeTableTable <- cbind(
  catTableAtThresh(df, rep(TRUE,nrow(df)),vars="household.income.full"),
  catTableAtThresh(df, df$ABCD_rsfmri_QC1,vars="household.income.full"),
  catTableAtThresh(df, df$any_rest,vars="household.income.full"),
  catTableAtThresh(df, df$gframes_0.5_375,vars="household.income.full"),
  catTableAtThresh(df, df$gframes_0.4_375,vars="household.income.full"),
  catTableAtThresh(df, df$gframes_0.3_375,vars="household.income.full"),
  catTableAtThresh(df, df$ABCD_rsfmri_QC2,vars="household.income.full"),
  catTableAtThresh(df, df$gframes_0.2_375,vars="household.income.full"),
  catTableAtThresh(df, df$gframes_0.1_375,vars="household.income.full")
)

#Try to draw as a huxtable
#rownames(FullIncomeTableTable)<-gsub("\\$","\\\\$",rownames(FullIncomeTableTable))
FullIncomeTableHux<-as_hux(FullIncomeTableTable) %>%
  theme_basic() %>%
  insert_row(value=c("n","\\%",rep(c("n","\\%"),8))) %>%
  insert_row("Full","",
             "QC1","",
             "ABCC","",
             ".5","",
             ".4","",
             ".3mm","",
             "QC2","",
             ".2mm","",
             ".1mm","") %>%
  merge_cells(1,1:2) %>%
  merge_cells(1,3:4) %>%
  merge_cells(1,5:6) %>%
  merge_cells(1,7:8) %>%
  merge_cells(1,9:10) %>%
  merge_cells(1,11:12) %>%
  merge_cells(1,13:14) %>%
  merge_cells(1,15:16) %>%
  merge_cells(1,17:18) %>% 
  insert_column(value=c("","",rownames(FullIncomeTableTable) %>% replace_na("Missing"))) %>%
  set_caption("Granular Household Income at Each Level of Stringency (Subjects excluded with < 375 Frames)") %>%
  set_escape_contents(FALSE)  %>%
  set_font_size(8) %>%
  set_number_format(3:nrow(.),2+0:7*2,value=fmt_pretty()) %>%
  set_number_format(3:nrow(.),3+0:7*2,value="%.2g") %>%
  set_all_padding(1)

FullIncomeTableHux
```

```{r}
#For models, place the modal level first and reformat labels.
df$household.income.full.ref<-relevel(df$household.income.full,9)
df$household.income.full.ref <- factor(df$household.income.full.ref,
                                               labels=c(
                                "\\$100k through \\newline \\$199.9k",
                                "Less than \\newline \\$5k",
                                "\\$5k through \\newline \\$11.9k",
                                "\\$12k through \\newline \\$15.9k",
                                "\\$16k through \\newline \\$24.9k",
                                "\\$25k through \\newline \\$34.9k",
                                "\\$35k through \\newline \\$49.9k",
                                "\\$50k through \\newline \\$74.9k",
                                "\\$75k through \\newline \\$99.9k",
                                "\\$200k and greater"
                              ))
  


m.bvincome<-bvmodel("household.income.full")
#Reformat the table:
# Replace the first \n with " ["
m.bvincome.f <- sub("\n", " [", m.bvincome, fixed = TRUE)
# Replace the second \n with "]"
m.bvincome.f <- sub("\n", "]", m.bvincome.f, fixed = TRUE)
# Remove the p value
m.bvincome.f <- gsub("].*","]", m.bvincome.f)


as_hux(m.bvincome.f) %>%
  insert_column(levels(df$household.income.full)[-1]) %>%
  insert_row(
    "Household Income (ref: \\$100-\\$199.9k)", rep(c("OR [95\\% CI]"), 8)) %>%
  insert_row(c("", "T", "C", ".5", ".4", ".3", "R", ".2", ".1")) %>% 
  set_caption("Bivariate Model of Granular Household Income and Missingness by Condition. Ref: \\$100k-\\$199k") %>% 
  set_escape_contents(value=FALSE) %>% 
  set_wrap(TRUE) %>% 
  set_width(1)

```

### Detailed Race/Ethnicity

Census Race/Ethnicity Categories were used in the manuscript for the sake of brevity and because they are conventional and easy to compare to other work (which is of primary importance in a work commenting on methods). However, we acknowledge that the census categories are reductive both in the number of identifications present and in the lack of nuance they present (i.e., inability to pick multiple categories). ABCD collects information on participant race/ethnicity in considerably more detail, specifically as a series of yes/no questions about particular identities. We here present a comparison tables between the two measures, descriptives of the more granular race/ethnicity data, and bivariate models using those variables.

#### Descriptives

Table 15 describes the many race/ethnicity endorsement variables available in ABCD, cross-referenced against the census race/ethnicity variable used in the manuscript.

```{r}
retable1<-df %>% select(race_ethnicity.factor:ethn.iden.hisp) %>%
  group_by(race_ethnicity.factor) %>%
  summarise(across(
    race.iden.white:ethn.iden.hisp,
    ~ mean(. == TRUE, na.rm = TRUE),
    .names = "percentage_{.col}"
  )) %>% as_hux() %>% set_number_format(2:nrow(.),2:ncol(.),value=fmt_percent()) %>%
  t() %>% set_caption("Percentage Endorsing Granular Race/Ethnicity Variables within Census Race/Ethnicity Groups")

retable1[,1] <- c("",
                  "White",
                  "Black",
                  "American Indian",
                  "Alaska Native",
                  "Native Hawaiian",
                  "Guamanian",
                  "Samoan",
                  "Pacific Islander",
                  "Asian Indian",
                  "Filipino",
                  "Chinese",
                  "Japanese",
                  "Korean",
                  "Vietnamese",
                  "Other Asian",
                  "Other",
                  "Refuse",
                  "Don't Know",
                  "Hispanic")  

retable1[,1:6] %>% 
  insert_row("","Census Race/Ethnicity","","","","") %>% 
  merge_cells(1,2:6)
```

Table 16 show descriptives of these variables by condition.

```{r}
boolTable<-\(data=df,bool=TRUE) {
  df[bool,] %>% summarise(across(race.iden.white:ethn.iden.hisp,
            list(n= ~ sum(.,na.rm = TRUE),
                 Percent = ~ round(mean(. == 1, na.rm = TRUE)*100,2)
                 ))) %>% 
    pivot_longer(cols=everything(),
                 names_to=c(".value","measure"),
                 names_sep="_") %>% t()
}

retable2 <- cbind(
  boolTable(bool = TRUE),
  boolTable(bool = df$ABCD_rsfmri_QC1),
  boolTable(bool = df$any_rest),
  boolTable(bool = df$gframes_0.5_375),
  boolTable(bool = df$gframes_0.4_375),
  boolTable(bool = df$gframes_0.3_375),
  boolTable(bool = df$ABCD_rsfmri_QC2),
  boolTable(bool = df$gframes_0.2_375),
  boolTable(bool = df$gframes_0.1_375))[-1,] 

retable2 %>%  as_hux() %>%
  set_number_format(1:nrow(.),seq(1,ncol(.),2),value=fmt_pretty()) %>% 
  set_number_format(1:nrow(.),seq(2,ncol(.),2),value=fmt_pretty(digits=2,format="f")) %>% 
  insert_column(c("White",
                  "Black",
                  "American Indian",
                  "Alaska Native",
                  "Native Hawaiian",
                  "Guamanian",
                  "Samoan",
                  "Pacific Islander",
                  "Asian Indian",
                  "Filipino",
                  "Chinese",
                  "Japanese",
                  "Korean",
                  "Vietnamese",
                  "Other Asian",
                  "Other",
                  "Refuse",
                  "Don't Know",
                  "Hispanic")) %>% 
  insert_row(c("",rep(c("n","%"),length(bools)))) %>% 
  insert_row(c("",
               "F","",
               "QC1","",
               "C","",
               ".5","",
               ".4","",
               ".3","",
               "QC2","",
               ".2","",
               ".1","")) %>% 
  set_caption("Granular Race/Ethnicity Data by Condition")

```

#### Bivariate Models

Finally, Tables 17-19 depict bivariate models for each race/ethnicity endorsement variable by condition.

```{r}
remodels<-lapply(names(df %>% select(race.iden.white:ethn.iden.hisp)),bvmodel,newline="\\newline ")

remodeltable<-as_hux(reduce(remodels,rbind)) %>%
  insert_column(c("White",
                  "Black",
                  "American Indian",
                  "Alaska Native",
                  "Native Hawaiian",
                  "Guamanian",
                  "Samoan",
                  "Pacific Islander",
                  "Asian Indian",
                  "Filipino",
                  "Chinese",
                  "Japanese",
                  "Korean",
                  "Vietnamese",
                  "Other Asian",
                  "Other",
                  "Refuse",
                  "Don't Know",
                  "Hispanic")) %>%
  insert_row(
    "", rep(c("OR\\newline [90\\% CI]\\newline p"), 8)) %>%
  insert_row(c("", "T", "C", ".5", ".4", ".3", "R", ".2", ".1")) %>%
  set_escape_contents(value=FALSE)  %>% 
  set_wrap(TRUE) %>% 
  set_width(1)


remodeltable[c(1:2,3:8),] %>% set_caption("Granular Race/Ethnicity Variables: Bivariate Models, Pt. 1") %>% set_label("gran.race.ethn.1") 
remodeltable[c(1:2,9:14),] %>% set_caption("Granular Race/Ethnicity Variables: Bivariate Models, Pt. 2") %>% set_label("gran.race.ethn.2") 
remodeltable[c(1:2,15:19),] %>% set_caption("Granular Race/Ethnicity Variables: Bivariate Models, Pt. 3") %>% set_label("gran.race.ethn.3") 
```

# Changes since pre-registration

The following changes were made to the analysis plan post-registration:

* BMI was added as a study variable, to enhance comparibility with Cosgrove et. al. (2020) and reflect the known relation between BMI and in-scanner motion.
* The Behavioral Inhibition scale was removed. It is not available in the ABCD baseline data and was included in error.
* More data was excluded prior to motion filtering than expected and there were more differences in inclusion criteria between ABCD versions than expected. Consequently, three 'QC' conditions were added in addition to the motion thresholds, to provide additional detail to inform study design.
* The originally planned approach to evaluate H2 was found to be infeasible (See 'H2 Model,' above). In practice, a visual inspection of the data did not support H2 (see H2 Marginal Means Plotting). Specifically, because so much data was missing, biases in the missing data were self-correcting as more data was excluded. I.e., in the event that males were more likely to be excluded than females (which appears to be true in this dataset), the bias is strongest as data is first excluded from the dataset. Once a significantly larger proportion of males have been excluded than females, the over-representation of females in the sample results in their being more likely to be excluded. At the extreme, when all of the data is excluded, there is no bias).

Here, we present the analyses originally proposed as written, excepting H2. Specifically, we present results from adjusted models without the BMI variable in the motion scrubbing conditions in Tables 20-21.

```{r}
model.h1prereg.5mm<-glm(!gframes_0.5_375 ~ sex + household.income + p.edu + race_ethnicity.factor + ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z + nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z ,data=df,family="binomial")
model.h1prereg.5mm.results<-cbind(confint(model.h1prereg.5mm,level=.95),model.h1prereg.5mm$coefficients)[,c(1,3,2)]
model.h1prereg.5mm.results<-cbind(model.h1prereg.5mm.results,pcorrect(coef(summary(model.h1prereg.5mm))[,4]))

model.h1prereg.4mm<-glm(
  !gframes_0.4_375 ~ sex + household.income + p.edu + race_ethnicity.factor + ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z + nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z ,
  data=df,
  family="binomial")
model.h1prereg.4mm.results<-cbind(confint(model.h1prereg.4mm,level=.95),model.h1prereg.4mm$coefficients)[,c(1,3,2)]
model.h1prereg.4mm.results<-cbind(model.h1prereg.4mm.results,pcorrect(coef(summary(model.h1prereg.4mm))[,4]))

model.h1prereg.3mm<-glm(
  !gframes_0.3_375 ~ sex + household.income + p.edu + race_ethnicity.factor + ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z + nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z ,
  data=df,
  family="binomial")
model.h1prereg.3mm.results<-cbind(confint(model.h1prereg.3mm,level=.95),model.h1prereg.3mm$coefficients)[,c(1,3,2)]
model.h1prereg.3mm.results<-cbind(model.h1prereg.3mm.results,pcorrect(coef(summary(model.h1prereg.3mm))[,4]))

model.h1prereg.2mm<-glm(
  !gframes_0.2_375 ~ sex + household.income + p.edu + race_ethnicity.factor + ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z + nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z ,
  data=df,
  family="binomial")
model.h1prereg.2mm.results<-cbind(confint(model.h1prereg.2mm,level=.95),model.h1prereg.2mm$coefficients)[,c(1,3,2)]
model.h1prereg.2mm.results<-cbind(model.h1prereg.2mm.results,pcorrect(coef(summary(model.h1prereg.2mm))[,4]))

model.h1prereg.1mm<-glm(
  !gframes_0.1_375 ~ sex + household.income + p.edu  + race_ethnicity.factor + ksads_factor + pds_category + adi.z + coi.z + nihtbx_flanker_agecorrected.z + nihtbx_cryst_agecorrected.z + nihtbx_totalcomp_agecorrected.z + pea_wiscv_tss.z + pfactor.z + INT.z + EXT.z + interview_age.z ,
  data=df,
  family="binomial")
model.h1prereg.1mm.results<-cbind(confint(model.h1prereg.1mm,level=.95),model.h1prereg.1mm$coefficients)[,c(1,3,2)]
model.h1prereg.1mm.results<-cbind(model.h1prereg.1mm.results,pcorrect(coef(summary(model.h1prereg.1mm))[,4]))
```

### Pre-registered Condition (Adjusted) Model Tables

```{r}
Mformat2<-\(m) {
  stars<-sdlabFunctions::starPs(m[,4])
  paste0(ORformat(m[,2]),
         stars,
         " [",ORformat(m[,1]),"-",ORformat(m[,3]),"]")
}

h1modelspreregtable<-cbind(
                     Mformat2(model.h1prereg.5mm.results),
                     Mformat2(model.h1prereg.4mm.results),
                     Mformat2(model.h1prereg.3mm.results),
                     Mformat2(model.h1prereg.2mm.results),
                     Mformat2(model.h1prereg.1mm.results))

#h1modelspreregtable <- gsub("\n", "\\newline", h1modelspreregtable)

h1modelspreregtable[h1modelspreregtable==".000"]<-"<.001"

alllevels<-c("Intercept",
      "Sex (Male)",
      "  $0-$25k",
      "  $25-$50k",
      "  $50-$75k",
      "  $75-$100k",
      "  >$200k",
      "  <High School",
      "  HS Grad.",
      "  Some College",
      "  Graduate",
      "  Black",
      "  Hispanic",
      "  Asian",
      "  Other",
      "  1 Trauma",
      "  >=2 Trauma",
      "  Early Puberty",
      "  Mid Puberty",
      "  Late Puberty",
      "  Post Pubertal",
      "Area Disadvantage",
      "Child Opportunity",
      "NIHTB Flanker",
      "NIHTB Crystalized",
      "NIHTB Total",
      "WISC V Matrix",
      "Psychopathology",
      "Internalizing",
      "Externalizing",
      "Age"
      )

h1prereghux<-as_hux(h1modelspreregtable) %>% 
  insert_column(alllevels) %>% 
  insert_row("Household Income (ref: $100-$200k)",after=2,colspan=6,fill="") %>% 
  insert_row("Highest Parental Education (ref: College Degree)",after=8,colspan=6,fill="") %>% 
  insert_row("Census Race/Ethnicity (ref: White)",after=13,colspan=6,fill="") %>% 
  insert_row("KSADS Trauma Count (ref: 0 Exposures)",after=18,colspan=6,fill="") %>% 
  insert_row("Pubertal Status (ref: pre-pubertal)",after=21,colspan=6,fill="") %>% 
  insert_row(c("Variable",rep(c("OR [95% CI]"),5)),after=0) %>% 
  insert_row(c("",".5",".4",".3",".2",".1")) %>%
  set_wrap(TRUE) %>%
  set_width(1) %>% 
  set_font_size(value=8)

colnames(h1prereghux)[1]<-"h1"

h1prereghux[c(1:2,3:20),] %>%
  set_caption("Adjusted Models Output, as Pre-registered (Pt. 1). ***: p<.001; **: p<.01; *:p<.05") %>% set_label("PreRegModel1")

h1prereghux[c(1:2,21:38),] %>%
  set_caption("Adjusted Models Output, as Pre-registered (Pt. 2). ***: p<.001; **: p<.01; *:p<.05") %>% set_label("PreRegModel2")
```

# Supplemental References

Achenbach, T. M., Dumenci, L., \& Rescorla, L. A. (2002). Ten-year comparisons of problems and competencies for national samples of youth: Self, parent, and teacher reports. \textit{Journal of Emotional and Behavioral Disorders, 10}(4), 194–203. \href{https://doi.org/10.1177/10634266020100040101}{doi:10.1177/10634266020100040101}

Akshoomoff, N., Beaumont, J. L., Bauer, P. J., Dikmen, S. S., Gershon, R. C., Mungas, D., Slotkin, J., Tulsky, D., Weintraub, S., Zelazo, P. D., \& Heaton, R. K. (2013). Nih Toolbox Cognition Battery (cb): Composite Scores of Crystallized, Fluid, and Overall Cognition. \textit{Monographs of the Society for Research in Child Development, 78}(4), 119–132. \href{https://doi.org/10.1111/mono.12038}{doi:10.1111/mono.12038}

Brislin, S. J., Martz, M. E., Joshi, S., Duval, E. R., Gard, A., Clark, D. A., Hyde, L. W., Hicks, B. M., Taxali, A., Angstadt, M., Rutherford, S., Heitzeg, M. M., \& Sripada, C. (2021). Differentiated nomological networks of internalizing, externalizing, and the general factor of psychopathology ('p factor’) in emerging adolescence in the ABCD study. \textit{Psychological Medicine}, 1–11. \href{https://doi.org/10.1017/S0033291720005103}{doi:10.1017/S0033291720005103}

Burley, D. T., Anning, K. L., \& van Goozen, S. H. M. (2022). The association between hyperactive behaviour and cognitive inhibition impairments in young children. \textit{Child Neuropsychology, 28}(3), 302–317. \href{https://doi.org/10.1080/09297049.2021.1976128}{doi:10.1080/09297049.2021.1976128}

Canivez, G. L., McGill, R. J., Dombrowski, S. C., Watkins, M. W., Pritchard, A. E., \& Jacobson, L. A. (2020). Construct Validity of the WISC-V in Clinical Cases: Exploratory and Confirmatory Factor Analyses of the 10 Primary Subtests. \textit{Assessment, 27}(2), 274–296. \href{https://doi.org/10.1177/1073191118811609}{doi:10.1177/1073191118811609}

Cheng, T. W., Magis-Weinberg, L., Guazzelli Williamson, V., Ladouceur, C. D., Whittle, S. L., Herting, M. M., Uban, K. A., Byrne, M. L., Barendse, M. E. A., Shirtcliff, E. A., \& Pfeifer, J. H. (2021). A Researcher’s Guide to the Measurement and Modeling of Puberty in the ABCD Study® at Baseline. \textit{Frontiers in Endocrinology, 12}. \href{https://www.frontiersin.org/articles/10.3389/fendo.2021.608575}{doi:10.3389/fendo.2021.608575}

Cosgrove, K. T., McDermott, T. J., White, E. J., Mosconi, M. W., Thompson, W. K., Paulus, M. P., Cardenas-Iniguez, C., \& Aupperle, R. L. (2022). Limits to the generalizability of resting-state functional magnetic resonance imaging studies of youth: An examination of ABCD Study® baseline data. \textit{Brain Imaging and Behavior, 16}(4), 1919–1925. \href{https://doi.org/10.1007/s11682-022-00665-2}{doi:10.1007/s11682-022-00665-2}

Clark, D. A., Hicks, B. M., Angstadt, M., Rutherford, S., Taxali, A., Hyde, L., Weigard, A., Heitzeg, M. M., \& Sripada, C. (2021). The General Factor of Psychopathology in the Adolescent Brain Cognitive Development (ABCD) Study: A Comparison of Alternative Modeling Approaches. In \textit{Clinical psychological science: A journal of the Association for Psychological Science, 9}(2), 169–182. \href{https://doi.org/10.1177/2167702620959317}{doi:10.1177/2167702620959317}

Evans, G. W., \& Kim, P. (2010). Multiple risk exposure as a potential explanatory mechanism for the socioeconomic status-health gradient: Multiple risk exposure and SES-health gradient. \textit{Annals of the New York Academy of Sciences, 1186}(1), 174–189. \href{https://doi.org/10.1111/j.1749-6632.2009.05336.x}{doi:10.1111/j.1749-6632.2009.05336.x}

Fadus, M. C., Valadez, E. A., Bryant, B. E., Garcia, A. M., Neelon, B., Tomko, R. L., \& Squeglia, L. M. (2021). Racial Disparities in Elementary School Disciplinary Actions: Findings From the ABCD Study. \textit{Journal of the American Academy of Child \& Adolescent Psychiatry, 60}(8), 998–1009. \href{https://doi.org/10.1016/j.jaac.2020.11.017}{doi:10.1016/j.jaac.2020.11.017}

Fan, C. C., Marshall, A., Smolker, H., Gonzalez, M. R., Tapert, S. F., Barch, D. M., Sowell, E., Dowling, G. J., Cardenas-Iniguez, C., Ross, J., Thompson, W. K., \& Herting, M. M. (2021). Adolescent Brain Cognitive Development (ABCD) study Linked External Data (LED): Protocol and practices for geocoding and assignment of environmental data. \textit{Developmental Cognitive Neuroscience, 52}, 101030. \href{https://doi.org/10.1016/j.dcn.2021.101030}{doi:10.1016/j.dcn.2021.101030}

Heeringa, S., \& Berglund, P. (2020). A Guide for Population-based Analysis of the Adolescent Brain Cognitive Development (ABCD) Study Baseline Data. \href{https://doi.org/10.1101/2020.02.10.942011}{doi:10.1101/2020.02.10.942011}

McLaughlin, K. A., Koenen, K. C., Hill, E. D., Petukhova, M., Sampson, N. A., Zaslavsky, A. M., \& Kessler, R. C. (2013). Trauma exposure and Posttraumatic Stress Disorder in a national sample of adolescents. \textit{Journal of the American Academy of Child and Adolescent Psychiatry, 52}(8), 815-830.e14. \href{https://doi.org/10.1016/j.jaac.2013.05.011}{doi:10.1016/j.jaac.2013.05.011}

Petersen, A. C., Crockett, L., Richards, M., \& Boxer, A. (1988). A self-report measure of pubertal status: Reliability, validity, and initial norms. \textit{Journal of Youth and Adolescence, 17}(2), 117–133. \href{https://doi.org/10.1007/BF01537962}{doi:10.1007/BF01537962}

Rakesh, D., Zalesky, A., \& Whittle, S. (2021). Similar but distinct – Effects of different socioeconomic indicators on resting state functional connectivity: Findings from the Adolescent Brain Cognitive Development (ABCD) Study®. \textit{Developmental Cognitive Neuroscience, 51}, 101005. \href{https://doi.org/10.1016/j.dcn.2021.101005}{doi:10.1016/j.dcn.2021.101005}

Saragosa-Harris, N. M., Chaku, N., MacSweeney, N., Guazzelli Williamson, V., Scheuplein, M., Feola, B., Cardenas-Iniguez, C., Demir-Lira, E., McNeilly, E. A., Huffman, L. G., Whitmore, L., Michalska, K. J., Damme, K. S., Rakesh, D., \& Mills, K. L. (2022). A practical guide for researchers and reviewers using the ABCD Study and other large longitudinal datasets. \textit{Developmental Cognitive Neuroscience, 55}, 101115. \href{https://doi.org/10.1016/j.dcn.2022.101115}{doi:10.1016/j.dcn.2022.101115}

Singh, G. K. (2003). Area Deprivation and Widening Inequalities in US Mortality, 1969–1998. \textit{American Journal of Public Health, 93}(7), 1137–1143. \href{https://doi.org/10.2105/AJPH.93.7.1137}{doi:10.2105/AJPH.93.7.1137}

Thompson, W. K., Barch, D. M., Bjork, J. M., Gonzalez, R., Nagel, B. J., Nixon, S. J., \& Luciana, M. (2019). The structure of cognition in 9 and 10 year-old children and associations with problem behaviors: Findings from the ABCD study’s baseline neurocognitive battery. \textit{Developmental Cognitive Neuroscience, 36}, 100606. \href{https://doi.org/10.1016/j.dcn.2018.12.004}{doi:10.1016/j.dcn.2018.12.004}

Townsend, L., Kobak, K., Kearney, C., Milham, M., Andreotti, C., Escalera, J., Alexander, L., Gill, M. K., Birmaher, B., Sylvester, R., Rice, D., Deep, A., \& Kaufman, J. (2020). Development of Three Web-Based Computerized Versions of the Kiddie Schedule for Affective Disorders and Schizophrenia Child Psychiatric Diagnostic Interview: Preliminary Validity Data. \textit{Journal of the American Academy of Child \& Adolescent Psychiatry, 59}(2), 309–325. \href{https://doi.org/10.1016/j.jaac.2019.05.009}{doi:10.1016/j.jaac.2019.05.009}

# SessionInfo

This output describes the environment in which the statistical code was run including package versions.

`r pander(sessionInfo())`
