---
title: "FastQC01 processing"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(pander)
```

This document processes abcd_fastqc01.txt and outputs table indicating whether participants have adequate useable data according to that source. The file must be saved in this folder.

# fastqc01

This file describes qc data in the fast track images from which the ABCC was derived.

```{r}
tnames<-read_tsv("abcd_fastqc01.txt",col_names=FALSE,n_max=1)
desc<-read_tsv("abcd_fastqc01.txt",col_names=FALSE,skip=1,n_max=1)
fastqc<-read_tsv("abcd_fastqc01.txt",skip=2,col_names=FALSE)
names(fastqc)<-t(tnames)
cbind(t(tnames),t(desc))
fastqc <- fastqc %>%
  select(c(subjectkey,visit,ftq_recalled,ftq_series_id,ftq_usable,ftq_notes,file_source))

privatize <- function(dataframe) {
  # This function removes subject id's from output
  # Step 1: Replace factors with character vectors
  factors_columns <- sapply(dataframe, is.factor)
  dataframe[factors_columns] <- lapply(dataframe[factors_columns], as.character)

  # Step 2: Replace character values matching regex with "sid_removed"
  regex_pattern1 <- "NDARMC[0-9A-Z]{6}"
  regex_pattern2 <- "NDARINV[0-9A-Z]{8}"
  dataframe <- lapply(dataframe, function(col) {
    if (is.character(col)) {
      col <- gsub(regex_pattern1, "sid_removed", col)
      col <- gsub(regex_pattern2, "sid_removed", col)
    }
    return(col)
  })

  return(dataframe)
}
```

The fastqc file is parsed and a few relevant columns are selected:

`r pander(head(fastqc) %>% privatize)`

Now we filter for baseline images and exclude recalled images (these have either been replaced or had consent withdrawn, and are not available).

```{r}
fastqc <- fastqc %>%
  filter(visit=="baseline_year_1_arm_1" & ftq_recalled==0)
```

Parse filenames to see what images are present per subject:

```{r}
fastqc <- fastqc %>%
  mutate(subjectkey=substr(ftq_series_id,0,15))
pattern <- "(?<=ABCD-).*?(?=_2)"

fastqc$imgtype<-stringr::str_extract(fastqc$ftq_series_id,pattern)

fastqc<-fastqc %>% filter(imgtype=="T1" |
                            imgtype=="T1-NORM" |
                            imgtype=="T2" |
                            imgtype=="T2-NORM" |
                            imgtype=="rsfMRI" |
                            imgtype=="fMRI-FM" |
                            imgtype=="fMRI-FM-PA" |
                            imgtype=="fMRI-FM-AP")

fastqc$imgtype <- as.factor(fastqc$imgtype)

dwndabledf<-fastqc %>%
  group_by(subjectkey, imgtype) %>%
  summarize(usecount=length(ftq_usable)) %>%
  pivot_wider(id_cols=subjectkey,names_from=imgtype,values_from=usecount)
dwndabledf <- dwndabledf %>% mutate(across(where(is.numeric),\(x) replace_na(x,0)))
```

This yields, e.g.:

`r pander(head(dwndabledf) %>% privatize())`

Participants with useable data will have a useable framemap, rs-fmri image, and T1. Here we construct a variable based on whether the user has enough images passing operator QC:

```{r}
useabledf<-fastqc %>%
  filter(ftq_usable==1) %>% 
  group_by(subjectkey, imgtype) %>%
  summarize(usecount=length(ftq_usable)) %>%
  pivot_wider(id_cols=subjectkey,names_from=imgtype,values_from=usecount)
useabledf <- useabledf %>% mutate(across(where(is.numeric),\(x) replace_na(x,0)))

useabledf$T1ok<- (useabledf$T1 + useabledf$`T1-NORM`)>0

#rsfmri needs to be present.

useabledf$rsfmriok<-useabledf$rsfMRI>0

#FM needs to be present, or the fm-ap and fm-pa are the same length and not equal to 0.

useabledf$fmok<- (useabledf$`fMRI-FM`>0) | (useabledf$`fMRI-FM-AP` > 0 & (useabledf$`fMRI-FM-AP` == useabledf$`fMRI-FM-PA`))

#We need all three

useabledf <- useabledf %>% 
  mutate(fastqcok = T1ok & rsfmriok & fmok) %>% 
        mutate(across(ends_with("ok"),\(x) replace_na(x,FALSE)))
```

# Inclusion Table

Output a table of participant inclusion flags.

```{r}
inclusion <- useabledf %>% 
  select(c(subjectkey,fastqcok,T1ok,rsfmriok,fmok)) %>% 
  mutate(fastqcok=replace_na(fastqcok,FALSE))

saveRDS(inclusion,file="imginclusion.Rds")
```

`r table(inclusion[,2:3])`

