---
title: "Appendix B"
author: "Matthew Peverill"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse); library(ggthemes); theme_set(theme_tufte())
library(pander)
library(hexbin)
```

From the ABCC, we need to import:

* Subject ID
* the average FD per functional scan.
* Do they have 5 minutes of usable data at each of the 5 included thresholds in the .mat file?
* The connectivity matrix for each threshold (or data to construct a plot with)
* A matrix of the distance between each pair of ROIs (in the template is fine).

# Index image files and extract mean FD

```{python, child='get_image_FD.py',eval=FALSE}
```

# Calculate the distance between Glasser Parcellation regions

These data were provided by Neurostars

# Sum total uncensored frames per threshold, per subject.

These are calculated per subject in a split by split basis. This code also incorporates the FD statistics, above.

```{r, child="process-split/processsplit.R",eval=FALSE}
```

## Merge:

```{r}
datapath=path.expand("./process-split/data/")
subjectRDSlist<-list.files(datapath,"abccsplit....subjectdata.RDS",full.names=TRUE,recursive=TRUE)
subjectdata <- lapply(subjectRDSlist, readRDS)
subjectdata <- Reduce(rbind,subjectdata)
saveRDS(subjectdata,"ABCCsubjectdata.RDS")
rm(subjectdata)
```

# Distance x correlation plots.

These are calculated by split by the following script:

```{r, child="process-split/processsplit2.R",eval=FALSE}
```

The resulting RDS objects for each split contain a list of five hexbin objects. These will need to be stacked.

```{r hexbinfunctions}
###############
## Functions ##
###############

# Hexbin concatenation
# Get elements from s4 object by name
get_slots <- function(x,nm) Map(\(c) getElement(x, c), nm)

# Unpack hexbin data to be merged in to a dataframe
# Strictly speaking we don't need the xy coordinates, but it is a good error
# check if we have the computation time available.
unpack_hexbin <- function(x) {
  cols <- c("cell", "count", "xcm", "ycm")
  return(cbind(data.frame(get_slots(x,cols)),
               hcell2xy(x)))
}

# Get columns from a dataframe that should not vary between hexbins to be
# merged.
getmeta_hexbin <- function(x) {
  varying=c("cell", "count", "xcm", "ycm", "call", "n", "ncells")
  other_slots <- setdiff(slotNames(x), varying)
  get_slots(x,other_slots)
}

# Center of mass calculation for two points, robust to missing data.
cm<-function(x1,x2,x1w,x2w) {
  i<-x1*x1w
  j<-x2*x2w
  w<-sum(x1w,x2w,na.rm=TRUE)
  return(sum(i,j,na.rm=TRUE)/w)
}

combine_hexbin <- function(a,b) {
  hm <- merge(unpack_hexbin(a),
              unpack_hexbin(b),
              by = c("cell","x","y"),
              all = TRUE)
  if(any(duplicated(hm$cell))) stop("Duplicate cell Id's detected: Do the hexbin objects have the same grid?")
  hm2 <- hm %>% rowwise() %>% mutate(
    count=sum(count.x,count.y,na.rm=TRUE),
    xcm=cm(xcm.x,xcm.y,count.x,count.y),
    ycm=cm(ycm.x,ycm.y,count.x,count.y)
  )
  do.call(new,
          c(list("hexbin"),
            as.list(hm2[,c("cell",
                           "count",
                           "xcm",
                           "ycm")]),
            list(n = sum(hm2$count),
                 ncells = length(hm2)),
            getmeta_hexbin(a),
            call = quote(call("merged hexbin", 1))
          ))
}

# Shortcut for matrix reading
matrix_read<-function(x) {as.matrix(read.csv(x,header=FALSE))[1:360,1:360]}
```

```{r}
hexbinRDSlist<-list.files(datapath,"abccsplit...hexlist.RDS",full.names=TRUE,recursive=TRUE)
hexbindata <- lapply(hexbinRDSlist, readRDS)
hexbins <- Reduce(\(x,y) list('0.1'=combine_hexbin(x[['0.1']],y[['0.1']]),
                              '0.2'=combine_hexbin(x[['0.2']],y[['0.2']]),
                              '0.3'=combine_hexbin(x[['0.3']],y[['0.3']]),
                              '0.4'=combine_hexbin(x[['0.4']],y[['0.4']]),
                              '0.5'=combine_hexbin(x[['0.5']],y[['0.5']]),
                              'none'=combine_hexbin(x[['none']],y[['none']])),
                  hexbindata)
saveRDS(hexbins,file="hexbinlist.RDS")
```

